### 2022-10-10 paper/paper.tex
JuliaCon 2022 Paper

\documentclass{juliacon}
\usepackage{amsmath}
\usepackage{float}
\setcounter{page}{1}

\begin{document}

\title{DisjunctiveProgramming.jl: Generalized Disjunctive Programming Models and Algorithms for JuMP}
\author{
  \large Hector D. Perez, Shivank Joshi, Ignacio E. Grossmann*
  \\\normalsize Carnegie Mellon University, Pittsburgh, PA, USA  
  \\\normalsize	*grossmann@cmu.edu
}

\maketitle

\section*{ABSTRACT}
We present a Julia package, \verb|DisjunctiveProgramming.jl|, that extends the functionality in \verb|JuMP.jl| to allow modeling problems via logical propositions and disjunctive constraints. Such models can then be reformulated into Mixed-Integer Programs (MIPs) that can be solved with the various MIP solvers supported by JuMP. To do so, logical propositions are converted to Conjunctive Normal Form (CNF) and reformulated into equivalent algebraic constraints. Disjunctions are reformulated into mixed-integer constraints via the reformulation technique specified by the user (Big-M or Hull reformulations). The package supports reformulations for disjunctions containing linear, quadratic, and nonlinear constraints.

\section*{Keywords}
JuMP, Mathematical Optimization, Generalized Disjunctive Programming

\section{Introduction}
The modeling of systems with discrete and continuous decisions is commonly done in algebraic form with mixed-integer programming (MIP) models. When the problems can be defined by purely linear constraints and a linear objective function, they are referred to as mixed-integer linear programs (MILP). When nonlinearities arrise in either the feasible space or the objective function, they are called mixed-integer nonlinear programs (MINLP).
\vskip 6pt
A more systematic approach to modeling such systems is to use Generalized Disjunctive Programming (GDP) \cite{chen_grossmann_2019, grossmann_trespalacios_2013}, which generalizes the Disjunctive Programming paradigm proposed by Balas \cite{balas_2018}. GDP enables the modeling of systems from a logic-based level of abstraction that captures the fundamental rules governing such systems via algebraic constraints and logic. This formulation is useful for expressing problems in an intuitive way that relies on their logical underpinnings without needing to introduce mixed-integer constraints. GDP models are often easier to understand as related constraints are grouped into disjuncts that describe clearly defined subsets of the feasible space. The models obtained via GDP can be reformulated into the pure algebraic form best suited for the application of interest.  It is also often possible to exploit the explicit logical structure of a GDP model to provide tighter relaxations than corresponding MIP models, which may improve convergence speed and robustness for solutions via advanced solution algorithms \cite{chen_grossmann_2019}.
\vskip 6pt
Within the optimization community, there is a high volume of ongoing research that relies on GDP to formulate models for a variety of applications. Due to the combinatorial nature of system design problems, the GDP paradigm has been applied to the synthesis of complex processes and networks \cite{MATOVU2022107856, ZHOU202269}, the planning and optimal control of energy systems \cite{CHO2022841, kim2022generalized}, and the modeling of chemical synthesis under uncertainty \cite{CHEN2022107616}. These and numerous other applications of GDP illustrate the benefit of having a robust package for GDP that removes much of the overhead associated with developing and testing GDP models. Although packages with GDP capabilities exist for \verb|Pyomo| \cite{chen2022pyomo} and \verb|GAMS| \cite{vecchietti1999logmip}, having such a package available in Julia can greatly accelerate research in optimization, where packages like \verb|JuMP.jl| \cite{dunning_huchette_lubin_2017} are gaining significant traction.
\vskip 6pt
This paper provides background on the GDP paradigm, and the techniques for reformulating and solving such models. It then presents the package \verb|DisjunctiveProgramming.jl| as an extension to \verb|JuMP.jl| for creating models for optimization that follow the GDP modeling paradigm and can be solved using the vast list of supported solvers \cite{DunningHuchetteLubin2017}. A case study demonstrates the use of the package for chemical process superstructure optimization.

\section{Generalized Disjunctive Programming}
The GDP form of modeling is an abstraction that uses both algebraic and logical constraints to capture the fundamental rules governing a system. The two main reformulation strategies to transform GDP models into their equivalent MIP models are the Big-M reformulation \cite{nemhauser_1999, TRESPALACIOS201598} and the Hull reformulation \cite{LEE20002125}, the latter of which yields tighter models at the expense of larger model sizes \cite{grossmann_lee_2003}. 
\vskip 6pt

\subsection{Model}

The general notation for a GDP problem is given in Eq. \eqref{eq:general_gdp} - \eqref{eq:general_gdp1}.
\begin{align}
    \label{eq:general_gdp}
    \min \ &f(x) \\
    \text{s.t.} \ &g(x) \leq 0 \\
    &\bigvee_{i \in J_k}
    \begin{bmatrix}
        Y_{ik} \\
        h_{ik}(x) \leq 0
    \end{bmatrix} \quad \forall k \in K \\
    & \Omega(Y) = true \\
    & Y_{ik} \in \{true, false\} \quad \forall i \in J_k, k \in K\\
    \label{eq:general_gdp1}
    & x \in X \subseteq \mathbb{R}^n
\end{align}
Here $f(x)$ is the objective function to be minimized over the continuous variable $x$, $g(x)$ represents the global constraints, $h(x)$ represents the disjunct-specific constraints, and $Y$ is the Boolean variable governing each disjunction. In this notation, there are $k$ disjunctions with $i$ disjuncts in each. Constraints $h_{ik}(x) \le 0$, are applied only if the Boolean indicator variable for the respective disjunct, $Y_{ik}$, is denoted as being active (i.e., \textit{true}) \cite{chen_grossmann_2019}. The set of logical constraints, $\Omega(Y)$, describe the logical relationships between the selections of indicator variables. These can take the form of logical propositions or constraint programming expressions.
\vskip 6pt

In the case of a linear objective function and constraint set, the GDP model can be written as Eq. \eqref{eq:lgdp} - \eqref{eq:lgdp2}.
\begin{align}
    \label{eq:lgdp}
    \min \ & c^Tx \\
    \text{s.t.} \ &Ax \leq b \\
    &\bigvee_{i \in J_k}
    \begin{bmatrix}
        Y_{ik} \\
       B_{ik}x \leq d_{ik}
    \end{bmatrix}, \quad \forall k \in K \\
    & \Omega(Y) = true \\
    \label{eq:lgdp2}
    & Y_{ik} \in \{true, false\} \quad \forall i \in J_k, k \in K
\end{align}
\vskip 6pt

\subsection{Linear GDP reformulation example}
The simplest example of a linear GDP system is given in \eqref{eq:ex} - \eqref{eq:y}, where $Y_i$ is a Boolean indicator variable that enforces the constraints in the disjunct ($Ax \le b$ or $Cx \le d$) when $true$.
\vskip 6pt
\begin{equation}
    \label{eq:ex}
    \begin{bmatrix}
    Y_1 \\ Ax \leq b
    \end{bmatrix}
    \lor
    \begin{bmatrix}
        Y_2 \\ Cx \leq d
    \end{bmatrix}
\end{equation}
\begin{equation}
    \label{eq:x}
    0 \leq x \leq U
\end{equation}
\begin{equation}
    \label{eq:simple_xor}
    Y_1 \ \underline{\vee} \ Y_2
\end{equation}
\begin{equation}
    \label{eq:y}
    Y_1, Y_2 \in \{true, false\}
\end{equation}
\vskip 6pt

For visualization purposes and without loss of generality, the simple linear example is used to illustrate the Big-M and Hull reformulations. Figure \ref{fig:reform_figure} illustrates the feasible space of a simple linear GDP with one disjunction and two continuous variables, $x_1$ and $x_2$. The rectangle on the left is described by the constraints in the left disjunct, $Ax \leq b$. The rectangle on the right is defined by the constraints in the right disjunct, $Cx \le d$. The non-overlapping nature of the two regions is supported by the exclusive-OR relationship in Eq. \eqref{eq:simple_xor}.

\begin{figure}%[H]
    \centering
    \includegraphics[scale=0.5]{solnspace.png}
    \caption{Feasible solution space for example disjunction}
    \label{fig:reform_figure}
\end{figure}
\vskip 6pt

 \subsubsection{Big-M Reformulation}
 The Big-M reformulation for this problem is given by \eqref{eq:x}, \eqref{eq:ex_bigm1} - \eqref{eq:ex_bigm4}, where $M$ is a sufficiently large scalar that makes the particular constraint redundant when its indicator variable is not selected (i.e., $y_i = 0$). Note that the Boolean variables, $Y_i$, are replaced by binary variables, $y_i$. When the integrality constraint in Eq. \eqref{eq:ex_bigm4} is relaxed to $0 \leq x_1, x_2 \leq 1$, the resulting feasible region can be visualized by projecting the relaxed model onto the $x_1, x_2$ plane. This results in the region encapsulated by the dashed line in Figure \ref{fig:bigm}. It should be noted that the relaxed feasible region is not as tight as possible around the original feasible solution space. The choice of the large $M$ value determines the tightness of this relaxation, and the minimal value of $M$ for the optimal relaxation can be found through interval arithmetic when the model is linear. For nonlinear models, the tightest $M$ can be obtained by solving the maximization problem $\{\max h_{ik}(x): x \in X\}$. An alternate method for tight Big-M relaxations is given in \cite{TRESPALACIOS201598}.

\begin{equation}
    \label{eq:ex_bigm1}
    Ax \leq b + M \cdot (1 - y_1)
\end{equation}
\begin{equation}
    \label{eq:ex_bigm2}
    Cx \leq d + M \cdot (1 - y_2)
\end{equation}
\begin{equation}
    \label{eq:ex_bigm3}
    y_1 + y_2 = 1
\end{equation}
\begin{equation}
    \label{eq:ex_bigm4}
    y_1, y_2 \in \{0,1\}
\end{equation}

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{bigm.png}
    \caption{Relaxed solution space using Big-M Reformulation}
    \label{fig:bigm}
\end{figure}

\subsubsection{Hull Reformulation}
The Hull reformulation is given by \eqref{eq:x}, \eqref{eq:ex_bigm3} - \eqref{eq:ex_hull3}, which requires lifting the model to a higher-dimensional space. When projected to the original space, the continuous relaxation of the model is tighter than its Big-M equivalent \cite{grossmann_trespalacios_2013}. The reformulation relaxation can be visualized by the region encapsulated by the dashed line in Figure \ref{fig:chr}. Note that this reformulation provides a tighter relaxation than the Big-M reformulation in Figure \ref{fig:bigm}. Also note that describing the geometry of this relaxation is more complex than the Big-M relaxation, which is made possible by the increased number of constraints and variables in the model.

\begin{equation}
    \label{eq:ex_hull1}
    Ax_1 \leq by_1
\end{equation}
\begin{equation}
    \label{eq:ex_hull0}
    Cx_2 \leq dy_2
\end{equation}
\begin{equation}
    \label{eq:ex_hull2}
    x = x_1 + x_2
\end{equation}
\begin{equation}
    \label{eq:ex_hull3}
    0 \leq x_i \leq U y_i \quad \forall i \in \{1,2\}
\end{equation}

\begin{figure}%[H]
    \centering
    \includegraphics[scale=0.5]{chr.png}
    \caption{Relaxed solution space using Hull Reformulation}
    \label{fig:chr}
\end{figure}
\vskip 6pt

\subsection{Logic constraint reformulation}

\subsubsection{Propositional Logic}
The logic propositions within the set of decision selection relationships, $\Omega$, must be converted into conjunctive normal form (CNF) to enable reformulating a GDP model as a MIP model. This means that each clause within the set of propositions must be formulated into a conjunction of disjunctions. This process can be accomplished by following the simplifying rules of propositional logic (De Morgan's laws). For boolean variables $A$, $B$, and $C$ the following rules are used for converting to CNF (in the order given below),
\begin{align*}
    A \leftrightarrow B & \text{ is replaced by } (A \rightarrow B) \land (B \rightarrow A) \\
    A \rightarrow B & \text{ is replaced by } \lnot A \lor B \\
    \lnot(A \lor B) & \text{ is replaced by } \lnot A \land \lnot B \\
    \lnot(A \land B) & \text{ is replaced by } \lnot A \lor \lnot B \\
    (A \land B) \lor C & \text{ is replaced by } (A \lor C) \land (B \lor C)
\end{align*}

Once the logic propositions are converted to CNF, each clause can be converted into an algebraic constraint with the following equivalence,

\begin{align*}
    \bigvee_{i \in I} Y_i & \ \ \text{becomes} \ \ \sum_{i\in I} y_i \geq 1 \\
\end{align*}

Alternate approaches exist for converting propositional logic statements into CNF, which involve preserving clause satisfiability rather than clause equivalence. These approaches prevent exponential size increase in clauses and yield logically consistent results \cite{jackson_sheridan_2005}.

\subsubsection{Constraint Programming}
The constraint-programming selection requirements for constraints within $\Omega$ are reformulated as follows,

\begin{align*}
    \text{exactly}(n, Y) & \ \ \text{becomes} \ \ n = \sum_i Y_i \\
    \text{atleast}(n, Y) &  \ \ \text{becomes} \ \ n \leq \sum_i Y_i \\
    \text{atmost}(n, Y) &  \ \ \text{becomes} \ \ n \geq \sum_i Y_i
\end{align*}

Exclusive-OR constraints as the one given in Eq. \eqref{eq:simple_xor} become constraints of the form $exactly(1,Y)$.
\vskip 6pt

\subsection{Solution Techniques}

\subsubsection{Disjunctive branch and bound}
The disjunctive branch and bound method closely mirrors the standard branch and bound approach for the solution of mixed-integer programming problems \cite{grossmann_lee_2003}. A search tree is initialized by solving the continuous relaxation of the Big-M or Hull reformulation of the original GDP to obtain a lower bound on the optimum. Branching is then done on the disjunction with an indicator binary variable closest to 1. Two nodes are created at this point: one where the respective indicator Boolean variable is fixed to $true$ (the disjunct is enforced) and another where it is fixed to $false$ (the disjunct is removed from the disjunction). Each node is reformulated and solved to obtain a candidate lower bound. If the solution to a node results in a feasible solution that satisfies all integrality constraints, the solution is an upper bound on the optimum. Any non-integral solutions that exceed an upper bound are pruned from the search tree. The process is repeated until the lower and upper bounds are within the desired tolerance.

\subsubsection{Logic-based outer approximation}
Logic-based outer approximation is another algorithm which mirrors a standard technique for solving mixed-integer nonlinear programming problems \cite{E.Grossmann2009}. This approach starts by identifying a set of reduced Non-Linear Programming (NLP) sub-problems obtained by fixing Boolean variables in the different disjunctions such that each disjunct is selected at least once across the set of sub-problems (set covering step). 
Each sub-problem is solved to obtain an upper bound and a feasible point, about which the objective and constraints of the original GDP are linearized, and solve the resulting problem (via direct reformulation to MILP or via disjunctive branch and bound) to find a lower bound. If the lower and upper bound solutions have not converged, the Boolean variables from the previous solution are fixed and the resulting NLP is solved to find a potentially tighter upper bound solution. The procedure is repeated until convergence is obtained.
\vskip 6pt

\subsubsection{Hybrid cutting planes}
The cutting planes method is an algorithm for tightening the relaxed solution space of a problem reformulated with Big-M before solving it by adding additional constraints which remove parts of the relaxed space that are disjoint from the actual feasible solution space. These "cuts" to the relaxed solution space are derived from the tighter, hull relaxation of the problem. This algorithm provides a middle-ground for the tradeoff between the complexity and corresponding computational expense of the Hull reformulation with the less tight Big-M reformulation. \cite{trespalacios_grossmann_2016}. 
\vskip 6pt

\section{DisjunctiveProgramming.jl}
The following section describes the features of the \verb|DisjunctiveProgramming.jl| package and illustrates its syntax with an example from the chemical processing industry for superstructure optimization. The use of nested disjunctions is also shown.

\subsection{Features}
\verb|DisjunctiveProgramming.jl| allows for defining JuMP models with disjunctions that are directly reformulated via Big-M or Hull methods via the \verb|@disjunction| macro or \verb|add_disjunction!| function. Big-M values can be specified either for the entire disjunction, for each disjunct, or for each constraint in each disjunct. Alternately, if the constraints are linear, the code can use the variable bounds to perform interval arithmetic on each constraint to determine the tightest possible $M$ value to use \cite{agarwal2010automating}. For nonlinear GDP constraints, the epsilon approximation formulation for the perspective function in the Hull reformulation is used \cite{furman_sawaya_grossmann_2020}. Users can specify an epsilon tolerance value to use. Perspective functions are generated by relying on manipulation of symbolic expressions via \verb|Symbolics.jl| \cite{10.1145/3511528.3511535}.

\vskip 6pt
Logical propositions can be added to JuMP models using expressions involving the disjunction indicator variables and the standard Boolean operators ($\Leftrightarrow, \Rightarrow, \vee, \wedge, \text{ and } \neg$) in an \verb|@proposition| macro. These are automatically converted into CNF and added as integer algebraic constraints to the model. The constraint programming constraints can also be added using the \verb|choose!| function. The expressions are also automatically reformulated into integer algebraic constraints.

\vskip 6pt
Nesting of disjunctions is also supported.

\subsection{Example}
To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.3.2), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}. In this problem a chemical plant with two candidate reactor technologies ($R_1$ and $R_2$) must be designed. If the second reactor technology is chosen, a separation system must also be installed, for which two separation technologies ($S_1$ and $S_2$) are available. The GDP model seeks to maximize the product flow ($F_7$), while discounting for reactor ($C_R$) and separator ($C_S$) installation costs as given in \eqref{eq:example_obj}, subject to the nested disjunction in \eqref{eq:example_gdp} and the global mass balances in \eqref{eq:example_global}
- \eqref{eq:example_global1}. The system variables are the flows on each stream $i$ ($F_i$) and the installation costs, with their respective bounds given in \eqref{eq:example_var1} - \eqref{eq:example_var3}. The fixed cost and process yield parameters are given by $\gamma$ and $\beta$, respectively.

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{superstructure_pfd.png}
    \caption{Illustrative superstructure optimization problem}
    \label{fig:superstruct_opt_diagram}
\end{figure}

\begin{equation}
    \label{eq:example_obj}
    \max F_7 - C_R - C_S
\end{equation}
\begin{equation}
    \label{eq:example_gdp}
    \begin{bmatrix}
        Y_{R1} \\
        F_6 = \beta_{R1} F_2 \\
        F_3 = 0 \\
        F_4 = 0 \\
        F_5 = 0 \\
        C_R = \gamma_{R1} \\
        CS = 0
    \end{bmatrix} \lor
    \begin{bmatrix}
        Y_{R2} \\
        F_2 = 0 \\
        F_6 = 0 \\
        F_4 = \beta_{R2} F_3 \\
        C_R = \gamma_{R2} \\
        \begin{bmatrix}
            Y_{S1} \\
            F5 = \beta_{S1} F_4 \\
            C_S = \gamma_{S1}
        \end{bmatrix} \lor
        \begin{bmatrix}
            Y_{S2} \\
            F5 = \beta_{S2} F_4 \\
            C_S = \gamma_{S2}
        \end{bmatrix}
    \end{bmatrix}
\end{equation}
\begin{equation}
    \label{eq:example_global}
    F_1 = F_2 + F_3
\end{equation}
\begin{equation}
    \label{eq:example_global1}
    F_7 = F_5 + F_6
\end{equation}
\begin{equation}
    \label{eq:example_var1}
    0 \leq F_i \leq 10 \quad \forall i \in \{1,...,7\}
\end{equation}
\begin{equation}
    \label{eq:example_var2}
    0 \leq C_S \leq C_S^{max}
\end{equation}
\begin{equation}
    \label{eq:example_var3}
    C_R^{min} \leq C_R \leq C_R^{max}
\end{equation}
\vskip 6pt

The above system can be modeled and reformulated via the Big-M reformulation using \verb|DisjunctiveProgramming.jl|. The resulting JuMP model is then optimized using the HiGHS open-source MILP solver \cite{huangfu2018parallelizing} as shown below.

\begin{enumerate}
    \item Create the JuMP model and define the model variables and global constraints (mass balances).
\begin{lstlisting}[language = Julia]
using DisjunctiveProgramming, JuMP, HiGHS

# create model
m = JuMP.Model(HiGHS.Optimizer)
# add variables to model
@variable(m, 0 <= F[i = 1:7] <= 10)
@variable(m, 0 <= CS <= CSmax)
@variable(m, CRmin <= CR <= CRmax)

# add constraints to model
@constraints(m,
    begin
        F[1] == F[2] + F[3]
        F[7] == F[5] + F[6]
    end
)
\end{lstlisting}
    \item Define the inner (nested) disjunction for the separation technologies in the superstructure using the \verb|@disjunction| macro.   
\begin{lstlisting}[language = Julia]
# define inner disjunction
@disjunction(m,
    begin
        F[5] == β[:S1]*F[4]
        CS == γ[:S1]
    end,
    begin
        F[5] == β[:S2]*F[4]
        CS == γ[:S2]
    end,
    reformulation = :big_m, # reformulation type
    name = :YS # symbol for indicator variable
)
\end{lstlisting}
    \item Define constraints in the outer disjunctions.
\begin{lstlisting}[language = Julia]
# define constraints in left disjunct
R1_con = @constraints(m,
    begin
        F[6] == β[:R1]*F[2]
        [i = 3:5], F[i] == 0
        CR == γ[:R1]
        CS == 0
    end
)

# define constraints in right disjunct
R2_con = @constraints(m,
    begin
        F[6] == β[:R2]*F[3]
        CR == γ[:R2]      
    end
)
\end{lstlisting}
    \item Build the main disjunction using the constraint blocks defined in (3) and the \verb|add_disjunction!| function. Note that the reformulated constraints for the nested disjunction are stored in the \verb|.ext| dictionary of the model under the name of the disjunction (\verb|:YS| in this case).
\begin{lstlisting}[language = Julia]
# add nested disjunction to model
add_disjunction!(m,
    R1_con,
    # general constraints in R2 disjunction
    (
        R2_con,
        m.ext[:YS] #reformulated inner disj.
    ),
    reformulation = :big_m, # reformulation type
    name = :YR # symbol for indicator variable
)
\end{lstlisting}
    \item Add the selection logical constraints using the \verb|choose!| function. The first constraint enforces that only one reactor is selected. The second constraint enforces that the separation system be defined only if the second reactor ($R_2$) is selected. This constraint is equivalent to $Y_{R_2} \Leftrightarrow Y_{S_1} \underline{\vee} Y_{S_2}$.
\begin{lstlisting}[language = Julia]
choose!(1, YR[1], YR[2]; mode = :exactly)
choose!(YR[2], YS[1], YS[2]; mode = :exactly)
\end{lstlisting}
    \item Add the objective function and optimize. 
\begin{lstlisting}[language = Julia]
@objective(m, Max, F[7] - CS - CR)
optimize!(m)
\end{lstlisting}
\end{enumerate}

\section{Future Work}
The next steps for the \verb|DisjunctivePrograming.jl| package rely on extending \verb|JuMP.jl| further to allow creating GDP models that are not necessarily reformulated at model creation. Such models will allow using the different GDP solution strategies, such as direct reformulation to MI(N)LP, disjunctive branch and bound, logic-based outer approximation, hybrid cutting planes, and basic steps. The updated package will leverage existing JuMP extension infrastructure and make it possible to define indexing notation for disjunctions, a new Boolean variable type, and a new disjunciton constraint type. These improvements are expected to make the package more usable, flexible, and performant for advanced applications of GDP in JuMP.

\section{Related Work}
The popular Python package \verb|Pyomo| \cite{bynum2021pyomo, hart2011pyomo} is widely used for optimization development and includes an extension for generalized disjunctive programming \cite{chen2022pyomo}. \verb|GAMS| \cite{Bussieck2004} is a widely used optimization modeling language with support for GDP under the \verb|GAMS EMP| solver that uses \verb|LogMIP| \cite{vecchietti1999logmip}. Research is also being conducted to integrate modern process simulation technology, such as \verb|Aspen|, within the GDP paradigm \cite{NAVARROAMOROS201413}.

\section{Conclusion}
\verb|DisjunctiveProgramming.jl| is an extension to \verb|JuMP| for creating models for optimization that are formulated according to the generalized disjunctive programming paradigm. The package provides several options for reformulations including the Big-M and Hull relaxations. This package can be used to model problems, reformulate them, and optimize them using existing mathematical programming infrastructure in \verb|JuMP|. This can be useful for industrial and academic applications of GDP, such as superstructure optimization. The capabilities of this package allow for this modeling paradigm to be exploited using \verb|Julia|'s efficient dynamically-typed systems for rapid development, building, and testing of optimization models.

% References
\input{bib.tex}

\end{document}

### 2022-10-10 paper/paper.tex
minor change
update xor
clarify CP text

@@
 
-\begin{figure}%[H]
+\begin{figure}
     \centering
@@
 \subsubsection{Constraint Programming}
-The constraint-programming selection requirements for constraints within $\Omega$ are reformulated as follows,
+Selection constraints analogous to those used in Constraint Programming (CP) can also be included in $\Omega(Y)$.
+These constraints are of the form "allow exactly $n$ elements in a list of Boolean variables to be $true$." This type of constraint overcomes the limitations of the Boolean exclusive-OR ($\underline{\vee}$) operator, which can only enforce that an odd number of elements in a list of Booleans be $true$.
+Other CP-like constraints can be obtained by replacing "exactly" with "at most" or "at least".
+These constraints are reformulated as follows,
 
@@
 
-Exclusive-OR constraints as the one given in Eq. \eqref{eq:simple_xor} become constraints of the form $exactly(1,Y)$.
-\vskip 6pt
+Exclusive-OR constraints as the one given in Eq. \eqref{eq:simple_xor} are more generally modeled as $exactly(1,\{Y_1,Y_2\})$.
 
@@
 The procedure is repeated until convergence is obtained.
-\vskip 6pt
 
@@
 \cite{trespalacios_grossmann_2016}.
-\vskip 6pt
 
@@
     \item Create the JuMP model and define the model variables and global constraints (mass balances).
+
 \begin{lstlisting}[language = Julia]
@@
 \begin{lstlisting}[language = Julia]
-# define inner disjunction
 @disjunction(m,
@@
 \begin{lstlisting}[language = Julia]
-# add nested disjunction to model
 add_disjunction!(m,
     R1_con,
-    # general constraints in R2 disjunction
     (
-        R2_con,
+        R2_con, #general constraints in R2 disj.
         m.ext[:YS] #reformulated inner disj.
@@
     \item Add the selection logical constraints using the \verb|choose!| function.
-The first constraint enforces that only one reactor is selected.
+The first constraint enforces that only one reactor is selected (i.e., $Y_{R_1} \ \underline{\vee} \ Y_{R_2}$).
 The second constraint enforces that the separation system be defined only if the second reactor ($R_2$) is selected.
-This constraint is equivalent to $Y_{R_2} \Leftrightarrow Y_{S_1} \underline{\vee} Y_{S_2}$.
+This constraint is equivalent to the proposition $Y_{R_2} \Leftrightarrow Y_{S_1} \ \underline{\vee} \ Y_{S_2}$.
 \begin{lstlisting}[language = Julia]

### 2022-10-11 paper/paper.tex
add note to CNF conversion

@@
 
-Once the logic propositions are converted to CNF, each clause can be converted into an algebraic constraint with the following equivalence,
+Once the logic propositions are converted to CNF, each clause can be converted into an algebraic constraint with the following equivalence (Note: any negated Boolean variables, $\neg Y_i$, are replaced with $1-y_i$ in the reformulation),
 

### 2022-10-11 src/bigm.jl
bug fixes: -don't disaggregate nested binaries -don't include nested binaries in big-M estimation

@@ -49,7 +49,7 @@ function infer_bigm(constr::ConstraintRef)
     #create a map of variables to their bounds
     bounds_dict = :variable_bounds_dict in keys(constr.model.ext) ? constr.model.ext[:variable_bounds_dict] : Dict()
     bounds_map = Dict(
-        var => get_bounds(var, bounds_dict)
+        var => is_binary(var) ? (0,0) : get_bounds(var, bounds_dict) #NOTE: ignore binaries in tight-M calculation
         for var in get_constraint_variables(constr)
     )
     #apply interval arithmetic

### 2022-10-11 src/hull.jl

@@ -17,6 +17,7 @@ function hull_reformulation!(constr::ConstraintRef{<:AbstractModel, MOI.Constrai
     bin_var_ref = constr.model[bin_var][i]
     #replace each variable with its disaggregated version
     for var_ref in get_constraint_variables(constr)
+        is_binary(var_ref) && continue #NOTE: binaries from nested disjunctions are not disaggregated and don't need to be swapped out
         #get disaggregated variable reference
         var_name_i = name_disaggregated_variable(var_ref, bin_var, i)
         var_i_ref = variable_by_name(constr.model, var_name_i)
@@ -81,6 +82,7 @@ function disaggregate_variables(m::Model, disj, bin_var)
     obj_dict = object_dictionary(m)
     bounds_dict = :variable_bounds_dict in keys(obj_dict) ? obj_dict[:variable_bounds_dict] : Dict() #NOTE: should pass as an keyword argument
     for var in var_refs
+        is_binary(var) && continue #NOTE: don't disaggregate binary variables from nested disjunctions
         #define UB and LB
         LB, UB = get_bounds(var, bounds_dict)
         #disaggregate variable and add bounding constraints

### 2022-10-11 src/logic.jl

@@ -10,7 +10,7 @@ function choose!(m::Model, n::Int, vars::VariableRef...; mode=:exactly, name="")
     add_selection!(m, n, vars...; mode, name)
 end
 function choose!(m::Model, var::VariableRef, vars::VariableRef...; mode=:exactly, name="")
-    @assert all(is_valid.(m, vcat(var,vars))) "Invalid VariableRefs passed."
+    @assert all(is_valid.(m, vcat(var,vars...))) "Invalid VariableRefs passed."
     add_selection!(m, var, vars...; mode, name)
 end
 function add_selection!(m::Model, n, vars::VariableRef...; mode::Symbol, name::String)

### 2022-10-11 src/utils.jl

@@ -206,3 +206,4 @@ Check if a constraint or tuple of constraints is valid.
 is_constraint(constr::ConstraintRef) = is_valid(constr.model,constr)
 is_constraint(constr::AbstractArray{<:ConstraintRef}) = all(is_constraint.(constr))
 is_constraint(constr::Tuple) = all(is_constraint.(constr))
+is_constraint(constr::Nothing) = false

### 2022-10-11 src/constraint.jl
bug fix when disjunct has single ConstraintRef Don't specify AbstractArray parameter type so m.ext can be used without splatting (nested disjunction)

@@ -29,7 +29,7 @@ end
 function check_constraint!(m::Model, constr_j::Tuple, constr_list::Vector)
     map(constr_jk -> check_constraint!(m, constr_jk, constr_list), constr_j)
 end
-function check_constraint!(m::Model, constr_j::AbstractArray{<:ConstraintRef}, constr_list::Vector)
+function check_constraint!(m::Model, constr_j::AbstractArray, constr_list::Vector)
     push!(constr_list, check_constraint!(m, constr_j))
 end
 function check_constraint!(m::Model, constr_j::ConstraintRef, constr_list::Vector)
@@ -45,7 +45,7 @@ function check_constraint!(m::Model, constr::ConstraintRef)
     end
     return new_constr
 end
-function check_constraint!(m::Model, constr::AbstractArray{<:ConstraintRef})
+function check_constraint!(m::Model, constr::AbstractArray)
     @assert all(is_valid.(m, constr)) "$constr is not a valid constraint."
     if !any(is_interval.(constr)) && !any(is_equalto.(constr))
         new_constr = constr

### 2022-10-11 src/reformulate.jl

@@ -17,10 +17,18 @@ function reformulate_disjunction(m::Model, disj...; bin_var, reformulation, para
     if reformulation == :hull
         disaggregate_variables(m, disj, bin_var)
     end
-    reformulate_disjunction(disj, bin_var, reformulation, param)
-    push!(m.ext[bin_var], Iterators.flatten(filter(i -> is_constraint(i), disj))...)
+    _reformulate_disjunction(disj, bin_var, reformulation, param)
+    for item in filter(is_constraint, disj)
+        if item isa ConstraintRef
+            push!(m.ext[bin_var], item)
+        else
+            append!(m.ext[bin_var], item)
+        end
+    end
+    # NOTE: Next line files when a disjunct has a single ConstraintRef since iterate is not defined for this type
+    # push!(m.ext[bin_var], Iterators.flatten(filter(is_constraint, disj))...)
 end
-function reformulate_disjunction(disj, bin_var, reformulation, param)
+function _reformulate_disjunction(disj, bin_var, reformulation, param)
     for (i,constr) in enumerate(disj)
         reformulate_constraint(constr, bin_var, reformulation, param, i)
     end
@@ -44,7 +52,7 @@ function reformulate_constraint(constr::Tuple, bin_var, reformulation, param, i)
         reformulate_constraint(constr_j, bin_var, reformulation, param, i, j)
     end
 end
-function reformulate_constraint(constr::AbstractArray{<:ConstraintRef}, bin_var, reformulation, param, i, j = missing)
+function reformulate_constraint(constr::AbstractArray, bin_var, reformulation, param, i, j = missing)
     for k in eachindex(constr)
         reformulate_constraint(constr[k], bin_var, reformulation, param, i, j, k)
     end

### 2022-10-11 src/utils.jl

@@ -204,6 +204,6 @@ constraint_variables(constr::AbstractDict) = Iterators.flatten(
 Check if a constraint or tuple of constraints is valid.
 """
 is_constraint(constr::ConstraintRef) = is_valid(constr.model,constr)
-is_constraint(constr::AbstractArray{<:ConstraintRef}) = all(is_constraint.(constr))
+is_constraint(constr::AbstractArray) = all(is_constraint.(constr))
 is_constraint(constr::Tuple) = all(is_constraint.(constr))
 is_constraint(constr::Nothing) = false

### 2022-10-12 src/constraint.jl
fix bugs to make more robust

@@ -30,6 +30,9 @@ function check_constraint!(m::Model, constr_j::Tuple, constr_list::Vector)
     map(constr_jk -> check_constraint!(m, constr_jk, constr_list), constr_j)
 end
 function check_constraint!(m::Model, constr_j::AbstractArray, constr_list::Vector)
+    map(constr_jk -> check_constraint!(m, constr_jk, constr_list), constr_j)
+end
+function check_constraint!(m::Model, constr_j::AbstractArray{<:ConstraintRef}, constr_list::Vector)
     push!(constr_list, check_constraint!(m, constr_j))
 end
 function check_constraint!(m::Model, constr_j::ConstraintRef, constr_list::Vector)
@@ -45,7 +48,7 @@ function check_constraint!(m::Model, constr::ConstraintRef)
     end
     return new_constr
 end
-function check_constraint!(m::Model, constr::AbstractArray)
+function check_constraint!(m::Model, constr::AbstractArray{<:ConstraintRef})
     @assert all(is_valid.(m, constr)) "$constr is not a valid constraint."
     if !any(is_interval.(constr)) && !any(is_equalto.(constr))
         new_constr = constr

### 2022-10-12 src/reformulate.jl

@@ -17,21 +17,15 @@ function reformulate_disjunction(m::Model, disj...; bin_var, reformulation, para
     if reformulation == :hull
         disaggregate_variables(m, disj, bin_var)
     end
-    _reformulate_disjunction(disj, bin_var, reformulation, param)
-    for item in filter(is_constraint, disj)
-        if item isa ConstraintRef
-            push!(m.ext[bin_var], item)
-        else
-            append!(m.ext[bin_var], item)
-        end
-    end
-    # NOTE: Next line files when a disjunct has a single ConstraintRef since iterate is not defined for this type
-    # push!(m.ext[bin_var], Iterators.flatten(filter(is_constraint, disj))...)
+    reformulate_disjunction(m, disj, bin_var, reformulation, param)
 end
-function _reformulate_disjunction(disj, bin_var, reformulation, param)
+function reformulate_disjunction(m::Model, disj, bin_var, reformulation, param)
     for (i,constr) in enumerate(disj)
         reformulate_constraint(constr, bin_var, reformulation, param, i)
     end
+    update_constraint_list!(disj, m.ext[bin_var])
+    # NOTE: Next line files when a disjunct has a single ConstraintRef since iterate is not defined for this type
+    # push!(m.ext[bin_var], Iterators.flatten(filter(is_constraint, disj))...)
 end
 
 """

### 2022-10-12 src/utils.jl

@@ -207,3 +207,21 @@ is_constraint(constr::ConstraintRef) = is_valid(constr.model,constr)
 is_constraint(constr::AbstractArray) = all(is_constraint.(constr))
 is_constraint(constr::Tuple) = all(is_constraint.(constr))
 is_constraint(constr::Nothing) = false
+
+"""
+    update_constraint_list!(disj, list::Vector)
+
+Update constraint list (for disjunction constraints stored in .ext Dict)
+"""
+function update_constraint_list!(disj, list::Vector)
+    disj_constraints = filter(is_constraint, disj)
+    for item in disj_constraints
+        update_constraint_list!(item, list)
+    end
+end
+function update_constraint_list!(item::AbstractArray{<:ConstraintRef}, list::Vector)
+    for idx in eachindex(item)
+        update_constraint_list!(item[idx], list)
+    end
+end
+update_constraint_list!(item::ConstraintRef, list::Vector) = push!(list, item)

### 2022-10-12 src/bigm.jl
fix bug when only positive BigM is passed by user (make it negative)

@@ -11,13 +11,16 @@ Perform Big-M reformulaiton on a nonlinear constraint at index k of constraint j
 
 Perform Big-M reformulation on a constraint at index k of constraint j in disjunct i.
 """
-function big_m_reformulation!(constr::ConstraintRef, bin_var, M, i, j, k)
-    M = get_reform_param(M, i, j, k; constr)
+function big_m_reformulation!(constr::ConstraintRef, bin_var, M0, i, j, k)
+    M = get_reform_param(M0, i, j, k; constr)
+    if !ismissing(M0) && constraint_object(constr).set isa MOI.GreaterThan && M > 0
+        M = -M #if a positive bigM value was provided and constraint is GreaterThan, use the negative of this number (-M*(1-y) <= func)
+    end
     add_to_function_constant(constr, -M)
-    set_normalized_coefficient(constr, constr.model[bin_var][i] , M)
+    set_normalized_coefficient(constr, constr.model[bin_var][i], M)
 end
-function big_m_reformulation!(constr::NonlinearConstraintRef, bin_var, M, i, j, k)
-    M = get_reform_param(M, i, j, k; constr)
+function big_m_reformulation!(constr::NonlinearConstraintRef, bin_var, M0, i, j, k)
+    M = get_reform_param(M0, i, j, k; constr)
     #create symbolic variables (using Symbolics.jl)
     for var_ref in get_constraint_variables(constr)
         symbolic_variable(var_ref)

### 2022-10-12 src/bigm.jl
bug fix

@@ -66,7 +66,7 @@ function infer_bigm(constr::ConstraintRef)
             end
         end
     elseif constr_set isa MOI.GreaterThan
-        M = -constr_st.lower
+        M = -constr_set.lower
         for (var,coeff) in constr_terms
             if coeff < 0
                 M += coeff*bounds_map[var][2]

### 2022-10-13 src/hull.jl
fix bug: don't disaggregate boolean variables and disaggregated vars (from nested disjunctions)

@@ -13,14 +13,20 @@ Call the hull reformulation on a constraint at index k of constraint j in disjun
 """
 function hull_reformulation!(constr::ConstraintRef{<:AbstractModel, MOI.ConstraintIndex{MOI.ScalarAffineFunction{T},V}}, bin_var, args...) where {T,V}
     #check constraint type
+    m = constr.model
     i = args[2] #get disjunct index
-    bin_var_ref = constr.model[bin_var][i]
+    bin_var_ref = m[bin_var][i]
     #replace each variable with its disaggregated version
-    for var_ref in get_constraint_variables(constr)
+    var_refs = setdiff(
+        get_constraint_variables(constr),
+        m.ext[:disaggregated_variables],
+        m.ext[:boolean_variables]
+    )
+    for var_ref in var_refs
         is_binary(var_ref) && continue #NOTE: binaries from nested disjunctions are not disaggregated and don't need to be swapped out
         #get disaggregated variable reference
         var_name_i = name_disaggregated_variable(var_ref, bin_var, i)
-        var_i_ref = variable_by_name(constr.model, var_name_i)
+        var_i_ref = variable_by_name(m, var_name_i)
         #check var_ref is present in the constraint
         coeff = normalized_coefficient(constr, var_ref)
         iszero(coeff) && continue #if not present, skip
@@ -76,7 +82,11 @@ Disaggregate all variables in the model and tag them with the disjunction name.
 """
 function disaggregate_variables(m::Model, disj, bin_var)
     #check that variables are bounded
-    var_refs = get_constraint_variables(disj)
+    var_refs = setdiff(
+        get_constraint_variables(disj),
+        m.ext[:disaggregated_variables],
+        m.ext[:boolean_variables]
+    )
     @assert all((has_upper_bound.(var_refs) .&& has_lower_bound.(var_refs)) .|| is_binary.(var_refs)) "All variables must be bounded to perform the Hull reformulation."
     #reformulate variables
     obj_dict = object_dictionary(m)
@@ -91,17 +101,21 @@ function disaggregate_variables(m::Model, disj, bin_var)
             var_name_i_str = name_disaggregated_variable(var,bin_var,i)
             var_name_i = Symbol(var_name_i_str)
             #create disaggregated variable
-            m[var_name_i] = add_disaggregated_variable(m, var, LB, UB, var_name_i_str)
[…]

### 2022-10-13 src/macros.jl

@@ -96,6 +96,12 @@ function add_disjunction!(m::Model,disj...;reformulation::Symbol,M=missing,ϵ=1e
         m[bin_var] = @variable(m, [eachindex(disj)], Bin, base_name = string(bin_var))
     end
 
+    #record boolean variable
+    if !in(:boolean_variables, keys(m.ext))
+        m.ext[:boolean_variables] = [] #store boolean variables to avoid disaggregating (nested disjunctions)
+    end
+    push!(m.ext[:boolean_variables], m[bin_var])
+
     #reformulate disjunction
     param = reformulation == :big_m ? M : ϵ
     reformulate_disjunction(m, disj...; bin_var, reformulation, param)

### 2022-10-13 src/reformulate.jl

@@ -10,11 +10,14 @@ Reformulate disjunction.
 function reformulate_disjunction(m::Model, disj...; bin_var, reformulation, param)
     #placeholder to store new constraints (reformulated)
     @assert !in(bin_var, keys(m.ext)) "$bin_var cannot be used as the indicator variable for the disjunction because it has already been used on another disjunction."
-    m.ext[bin_var] = []
+    m.ext[bin_var] = [] #store constraints associated with indicator variable
     #check disj
     disj = [check_constraint!(m, constr) for constr in disj]#check_disjunction!(m, disj)
     #run reformulation
     if reformulation == :hull
+        if !in(:disaggregated_variables, keys(m.ext))
+            m.ext[:disaggregated_variables] = [] #record disaggregated variables to avoid duplicating disaggregation (nested disjunctions)
+        end
         disaggregate_variables(m, disj, bin_var)
     end
     reformulate_disjunction(m, disj, bin_var, reformulation, param)

### 2022-10-13 paper/paper.tex
update version in paper

@@
 \subsection{Example}
-To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.3.2), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}.
+To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.3.3), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}.
 In this problem a chemical plant with two candidate reactor technologies ($R_1$ and $R_2$) must be designed.

### 2022-12-24 test/linear_constraint_tests.jl
Delete linear_constraint_tests.jl
focus on the paper for now

@@ -1,137 +1,0 @@
-using Test
-using JuMP
-using DisjunctiveProgramming
-using Symbolics
-
-@testset "linear constraints" begin
-
-    function minimal()
-        m = Model()
-        @variable(m, -1<=x<=10)
-        
-        @constraint(m, con1, x<=3)
-        @constraint(m, con2, 0<=x)
-        @constraint(m, con3, x<=9)
-        @constraint(m, con4, 5<=x)
-        
-        @disjunction(m,(con1,con2),con3,con4,reformulation=:CHR,name=:y)
-
-        @test true
-    end
-    
-    function simple_example(reform)
-        m = Model()
-        @variable(m, -10<=x<=10)
-        @constraint(m, con1, x<=-1)
-        @constraint(m, con2, 1<=x)
-        
-        if (reform == :BMR)
-            @disjunction(m, con1, con2, reformulation=:BMR, name=:y)
-        elseif (reform == :CHR)
-            @disjunction(m, con1, con2, reformulation=:CHR, name=:y)
-        end
-        return m
-    end
-
-    function robustness()
-        unreg = m -> unregister(m, :original_model_variables)
-
-        function fresh_model()
-            m = Model()
-            @variable(m, -10<=x<=10)
-            @constraint(m, con1, x<=-1)
-            @constraint(m, con2, 1<=x)
-            return m, con1, con2
-        end
-        
-        # not enough constraints
-        m = fresh_model()[1]
-        # @test_throws DomainError @disjunction(m, (con1, con2), reformulation=:BMR, name=:y)
-        unreg(m)
-        # @test_throws DomainError @disjunction(m, con1, reformulation=:BMR, name=:y)
-
-        # Big-M reformulation without variable bounds defined 
-        # should only work if user specifies M value
-        m = Model()
-        @variable(m, x)
-        @constraint(m, con1, x<=-1)
-        @constraint(m, con2, 1<=x)
-        @test @disjunction(m, con1, con2, reformulation=:BMR, name=:y, M=11) == nothing
-        unreg(m)
-        @test_throws ErrorException @disjunction(m, con1, con2, reformulation=:BMR, name=:y)
-
-        # CHR reformulation without variable bounds defined should fail
-        m = Model()
-        @variable(m, x)
[…]

### 2022-12-24 paper/paper.tex

@@
 This paper provides background on the GDP paradigm, and the techniques for reformulating and solving such models.
-It then presents the package \verb|DisjunctiveProgramming.jl| as an extension to \verb|JuMP.jl| for creating models for optimization that follow the GDP modeling paradigm and can be solved using the vast list of supported solvers \cite{DunningHuchetteLubin2017}.
+It then presents the package \verb|DisjunctiveProgramming.jl| as an extension to \verb|JuMP.jl| for creating models for optimization that follow the GDP modeling paradigm and can be solved using the vast list of supported solvers \cite{dunning_huchette_lubin_2017}.
 A case study demonstrates the use of the package for chemical process superstructure optimization.

### 2023-05-11 src/datatypes.jl
add default BigM; add general GDPData method

@@ -232,6 +232,9 @@ A type for using the big-M reformulation approach for disjunctive constraints.
 """
 struct BigM <: AbstractReformulationMethod
     value::Real
+    function BigM()
+        new(1e9)
+    end
 end # TODO add fields if needed
 
 """
@@ -266,5 +269,8 @@ mutable struct GDPData
             nothing,
             false
             )
+    end
+    function GDPData(args...)
+        new(args...)
     end
 end

### 2023-05-11 src/model.jl
extend copy_extension_data

@@ -37,6 +37,16 @@ function disjunctions(model::JuMP.Model)
     return model.ext[:GDP].disjunctions
 end
 
+function JuMP.copy_extension_data(data::GDPData, new_model::JuMP.AbstractModel, model::JuMP.AbstractModel)
+    new_model.ext[:GDP] = GDPData(
+        data.logical_variables, 
+        data.disjunctions, 
+        data.propositions, 
+        data.solution_method, 
+        data.ready_to_optimize
+    )
+end
+
 # Determine if the model is ready to call `optimize!` without a optimize hook
 _ready_to_optimize(model::JuMP.Model) = gdp_data(model).ready_to_optimize
 

### 2023-05-11 examples/ex1.jl
update example

@@ -1,34 +1,82 @@
 using JuMP
 using DisjunctiveProgramming
 
-m = Model()
-@variable(m, -5 ≤ x ≤ 10)
-@disjunction(
-    m,
-    0 ≤ x ≤ 3,
-    5 ≤ x ≤ 9,
-    reformulation=:big_m,
-    name=:y
+#TODO: Add proposition for exactly 1 disjunct selected
+
+## Model 1: 
+#   1 variable: x
+#   1 disjunction:
+#       2 disjuncts: 
+#           1st disjucnt: MOI.Interval linear constraint (1)
+#           2nd disjunct: MOI.GreaterThan & MOI.LessThan linear constraints (2)
+
+m = GDPModel()
+@variable(m, -10 ≤ x ≤ 10)
+@variable(m, Y[1:2], LogicalVariable)
+disjunct_1 = Disjunct(
+    tuple(
+        build_constraint(error, 1*x, MOI.Interval(0,3))
+    ),
+    Y[1]
 )
-@proposition(m, y[1] ∨ y[2]) #this is a redundant proposition
-
+disjunct_2 = Disjunct(
+    tuple(
+        build_constraint(error, 1*x, MOI.GreaterThan(5)),
+        build_constraint(error, 1*x, MOI.LessThan(9))
+    ),
+    Y[2]
+)
+disjunction = add_constraint(m, 
+    build_constraint(error, [disjunct_1, disjunct_2]),
+    "Disjunction"
+)
 print(m)
-
-# ┌ Warning: disj_y[1] : x in [0.0, 3.0] uses the `MOI.Interval` set. Each instance of the interval set has been split into two constraints, one for each bound.
-# ┌ Warning: disj_y[2] : x in [5.0, 9.0] uses the `MOI.Interval` set. Each instance of the interval set has been split into two constraints, one for each bound.
 # Feasibility
 # Subject to
-#  XOR(disj_y) : y[1] + y[2] == 1.0         <- XOR constraint
-#  y[1] ∨ y[2] : y[1] + y[2] >= 1.0         <- reformulated logical proposition (name is the proposition)
-#  disj_y[1,lb] : -x + 5 y[1] <= 5.0       <- left-side of constraint in 1st disjunct (name is assigned to disj_y[1][lb])
[…]

### 2023-05-11 examples/ex1.jl
update example 1

@@ -46,11 +46,7 @@ print(m)
 #  x + 7 Y[1] <= 10.0
 #  x + Y[2] <= 10.0
 #  x >= -10.0
-#  Y[1] >= 0.0
-#  Y[2] >= 0.0
 #  x <= 10.0
-#  Y[1] <= 1.0
-#  Y[2] <= 1.0
 #  Y[1] binary
 #  Y[2] binary
 
@@ -69,13 +65,9 @@ print(m)
 #  -3 Y[1] + x_Y[1] <= 0.0
 #  -9 Y[2] + x_Y[2] <= 0.0
 #  x >= -10.0
-#  Y[1] >= 0.0
-#  Y[2] >= 0.0
 #  x_Y[1] >= -10.0
 #  x_Y[2] >= -10.0
 #  x <= 10.0
-#  Y[1] <= 1.0
-#  Y[2] <= 1.0
 #  x_Y[1] <= 10.0
 #  x_Y[2] <= 10.0
 #  Y[1] binary

### 2023-05-11 src/hull.jl
remove bounds on binary indicator vars

@@ -30,8 +30,6 @@ function _disaggregate_variables(model::JuMP.Model, disj::DisjunctiveConstraintD
         bvar = JuMP.@variable(model, 
             base_name = string(d.indicator), 
             binary = true, 
-            lower_bound = 0, 
-            upper_bound = 1
         )
         model[Symbol(d.indicator,"_Bin")] = bvar
     end

### 2023-05-11 src/reformulate.jl

@@ -15,9 +15,7 @@ function _reformulate(model::JuMP.Model, method::BigM, disj::DisjunctiveConstrai
         #create binary variable for logic variable (indicator)
         bvar = JuMP.@variable(model, 
             base_name = string(d.indicator), 
-            binary = true, 
-            lower_bound = 0, 
-            upper_bound = 1
+            binary = true,
         )
         _reformulate(model, method, d, bvar)
     end

### 2023-05-11 src/variables.jl
extend methods for LogicVariableRef

@@ -65,6 +65,11 @@ JuMP.owner_model(vref::LogicalVariableRef) = vref.model
 """
 JuMP.index(vref::LogicalVariableRef) = vref.index
 
+function Base.:(==)(v::LogicalVariableRef, w::LogicalVariableRef)
+    return v.model === w.model && v.index == w.index
+end
+JuMP.isequal_canonical(v::LogicalVariableRef, w::LogicalVariableRef) = v == w
+
 """
 
 """

### 2023-05-11 src/datatypes.jl
change LogicalIndex to LogicalVariableIndex (since JuMP uses VariableIndex)

@@ -29,14 +29,14 @@ mutable struct LogicalVariableData
 end
 
 """
-    LogicalIndex
+    LogicalVariableIndex
 
 A type for storing the index of a [`LogicalVariable`](@ref).
 
 **Fields**
 - `value::Int64`: The index value.
 """
-struct LogicalIndex
+struct LogicalVariableIndex
     value::Int64
 end
 
@@ -47,7 +47,7 @@ A type for looking up logical variables.
 """
 struct LogicalVariableRef <: JuMP.AbstractVariableRef
     model::JuMP.Model
-    index::LogicalIndex
+    index::LogicalVariableIndex
 end
 
 """
@@ -187,8 +187,8 @@ end
 
 ## Extend the CleverDicts key access methods
 # index_to_key
-function _MOIUC.index_to_key(::Type{LogicalIndex}, index::Int64)
-    return LogicalIndex(index)
+function _MOIUC.index_to_key(::Type{LogicalVariableIndex}, index::Int64)
+    return LogicalVariableIndex(index)
 end
 function _MOIUC.index_to_key(::Type{DisjunctionIndex}, index::Int64)
     return DisjunctionIndex(index)
@@ -198,7 +198,7 @@ function _MOIUC.index_to_key(::Type{PropositionIndex}, index::Int64)
 end
 
 # key_to_index
-function _MOIUC.key_to_index(key::LogicalIndex)
+function _MOIUC.key_to_index(key::LogicalVariableIndex)
     return key.value
 end
 function _MOIUC.key_to_index(key::DisjunctionIndex)
@@ -252,7 +252,7 @@ The core type for storing information in a [`GDPModel`](@ref).
 """
 mutable struct GDPData
     # Objects
-    logical_variables::_MOIUC.CleverDict{LogicalIndex, LogicalVariableData}
+    logical_variables::_MOIUC.CleverDict{LogicalVariableIndex, LogicalVariableData}
     disjunctions::_MOIUC.CleverDict{DisjunctionIndex, DisjunctiveConstraintData}
     propositions::_MOIUC.CleverDict{PropositionIndex, PropositionData}
     
@@ -263,7 +263,7 @@ mutable struct GDPData
 
     # Default constructor
     function GDPData()
-        new(_MOIUC.CleverDict{LogicalIndex, LogicalVariableData}(),
+        new(_MOIUC.CleverDict{LogicalVariableIndex, LogicalVariableData}(),
[…]

### 2023-05-11 src/variables.jl
extend getindex to allow copying GDPModel

@@ -70,6 +70,10 @@ function Base.:(==)(v::LogicalVariableRef, w::LogicalVariableRef)
 end
 JuMP.isequal_canonical(v::LogicalVariableRef, w::LogicalVariableRef) = v == w
 
+function Base.getindex(map::JuMP.ReferenceMap, vref::LogicalVariableRef)
+    return LogicalVariableRef(map.model, JuMP.index(vref))
+end
+
 """
 
 """

### 2023-05-11 examples/ex1.jl
update ex1 and ex2

@@ -11,7 +11,7 @@ using DisjunctiveProgramming
 #           2nd disjunct: MOI.GreaterThan & MOI.LessThan linear constraints (2)
 
 m = GDPModel()
-@variable(m, -10 ≤ x ≤ 10)
+@variable(m, -5 ≤ x ≤ 10)
 @variable(m, Y[1:2], LogicalVariable)
 disjunct_1 = Disjunct(
     tuple(
@@ -33,7 +33,7 @@ disjunction = add_constraint(m,
 print(m)
 # Feasibility
 # Subject to
-#  x >= -10.0
+#  x >= -5.0
 #  x <= 10.0
 
 ##
@@ -41,11 +41,11 @@ DisjunctiveProgramming._reformulate(m, BigM())
 print(m)
 # Feasibility
 # Subject to
-#  x - 10 Y[1] >= -10.0
-#  x - 15 Y[2] >= -10.0
+#  x - 5 Y[1] >= -5.0
+#  x - 10 Y[2] >= -5.0
 #  x + 7 Y[1] <= 10.0
 #  x + Y[2] <= 10.0
-#  x >= -10.0
+#  x >= -5.0
 #  x <= 10.0
 #  Y[1] binary
 #  Y[2] binary
@@ -58,15 +58,15 @@ print(m)
 #  x - x_Y[1] - x_Y[2] == 0.0
 #  x_Y[1] >= 0.0
 #  -5 Y[2] + x_Y[2] >= 0.0
-#  -10 Y[1] - x_Y[1] <= 0.0
+#  -5 Y[1] - x_Y[1] <= 0.0
 #  -10 Y[1] + x_Y[1] <= 0.0
-#  -10 Y[2] - x_Y[2] <= 0.0
+#  -5 Y[2] - x_Y[2] <= 0.0
 #  -10 Y[2] + x_Y[2] <= 0.0
 #  -3 Y[1] + x_Y[1] <= 0.0
 #  -9 Y[2] + x_Y[2] <= 0.0
-#  x >= -10.0
-#  x_Y[1] >= -10.0
-#  x_Y[2] >= -10.0
+#  x >= -5.0
+#  x_Y[1] >= -5.0
+#  x_Y[2] >= -5.0
 #  x <= 10.0
 #  x_Y[1] <= 10.0
 #  x_Y[2] <= 10.0

### 2023-05-11 examples/ex2.jl

@@ -2,41 +2,89 @@
 using JuMP
 using DisjunctiveProgramming
 
-m = Model()
+m = GDPModel()
 @variable(m, -5 ≤ x[1:2] ≤ 10)
-@disjunction(
-    m,
-    begin
-        con1[i=1:2], 0 ≤ x[i] ≤ [3,4][i]
-    end,
-    begin
-        con2[i=1:2], [5,4][i] ≤ x[i] ≤ [9,6][i]
-    end,
-    reformulation = :big_m,
-    name = :y
+@variable(m, Y[1:2], LogicalVariable)
+disjunct_1 = Disjunct(
+    (
+        build_constraint(error, 1*x[1], MOI.Interval(0,3)),
+        build_constraint(error, 1*x[2], MOI.Interval(0,4))
+    ),
+    Y[1]
+)
+disjunct_2 = Disjunct(
+    (
+        build_constraint(error, 1*x[1], MOI.Interval(5,9)),
+        build_constraint(error, 1*x[2], MOI.Interval(4,6))
+    ),
+    Y[2]
+)
+disjunction = add_constraint(m, 
+    build_constraint(error, [disjunct_1, disjunct_2]),
+    "Disjunction"
 )
 print(m)
-
-# ┌ Warning: [con1[1] : x[1] in [0.0, 3.0], con1[2] : x[2] in [0.0, 4.0]] uses the `MOI.Interval` set. Each instance of the interval set has been split into two constraints, one for each bound.
-# ┌ Warning: [con2[1] : x[1] in [5.0, 9.0], con2[2] : x[2] in [4.0, 6.0]] uses the `MOI.Interval` set. Each instance of the interval set has been split into two constraints, one for each bound.
 # Feasibility
 # Subject to
-#  XOR(disj_y) : y[1] + y[2] == 1.0         <- XOR constraint
-#  con1[1,lb] : -x[1] + 5 y[1] <= 5.0      <- left-side of con1[1]
-#  con1[1,ub] : x[1] + 7 y[1] <= 10.0      <- right-side of con1[1]
-#  con1[2,lb] : -x[2] + 5 y[1] <= 5.0      <- left-side of con1[2]
[…]

### 2023-05-12 src/model.jl
copy_extension_data needs more work

@@ -38,13 +38,18 @@ function disjunctions(model::JuMP.Model)
 end
 
 function JuMP.copy_extension_data(data::GDPData, new_model::JuMP.AbstractModel, model::JuMP.AbstractModel)
-    new_model.ext[:GDP] = GDPData(
-        data.logical_variables, 
-        data.disjunctions, 
-        data.propositions, 
-        data.solution_method, 
-        data.ready_to_optimize
-    )
+    model_data = gdp_data(model)
+    #TODO need to copy disjunction constraints over to the new model
+    #   (maybe something similar to what is done in copy_to in MOI.jl/src/Utilities/copy.jl).
+    #   Otherwise, the constraints inside the disjuncts are not owned by the new model...
+    
+    # new_model.ext[:GDP] = GDPData(
+    #     data.logical_variables, 
+    #     data.disjunctions, 
+    #     data.propositions, 
+    #     data.solution_method, 
+    #     data.ready_to_optimize
+    # )
 end
 
 # Determine if the model is ready to call `optimize!` without a optimize hook

### 2023-10-11 examples/ex3.jl
merge https://github.com/pulsipher/DisjunctiveProgramming.jl/tree/structure_overall

@@ -1,43 +1,57 @@
 using JuMP
 using DisjunctiveProgramming
 
-m = Model()
+m = GDPModel()
 @variable(m, -5 ≤ x ≤ 10)
-@variable(m, z[i = 1:2], Bin)
-@disjunction(
-    m,
-    begin
-        con1A, exp(x) ≤ 2
-        con1B, -3 ≤ x
-    end,
-    begin
-        con2A, 3 ≤ exp(x)
-        con2B, 5 ≤ x
-    end,
-    reformulation=:hull,
-    name=:z
-)
-choose!(m, 1, z...; mode = :exactly, name = "XOR") #XOR constraint
+@variable(m, Y[1:2], LogicalVariable)
+@constraint(m, exp(x) <= 2, DisjunctConstraint(Y[1]))
+@constraint(m, x >= -3, DisjunctConstraint(Y[1]))
+@constraint(m, exp(x) >= 3, DisjunctConstraint(Y[2]))
+@constraint(m, x >= 5, DisjunctConstraint(Y[2]))
+@disjunction(m, Y)
+@constraint(m, Y in Exactly(1)) #logical constraint
+@objective(m, Max, x)
 print(m)
-
-# Feasibility
+# Max x
 # Subject to
-#  XOR(disj_z) : z[1] + z[2] == 1.0             <- XOR constraint
-#  x_z_aggregation : x - x_z1 - x_z2 == 0.0     <- aggregation of disaggregated variables
-#  x_z1_lb : -5 z[1] - x_z1 <= 0.0              <- lower-bound constraint on disaggregated variable x_z1 (x in 1st disjunct)
-#  x_z1_ub : -10 z[1] + x_z1 <= 0.0             <- upper-bound constraint on disaggregated variable x_z1 (x in 1st disjunct)
-#  x_z2_lb : -5 z[2] - x_z2 <= 0.0              <- lower-bound constraint on disaggregated variable x_z2 (x in 2nd disjunct)
-#  x_z2_ub : -10 z[2] + x_z2 <= 0.0             <- upper-bound constraint on disaggregated variable x_z2 (x in 2nd disjunct)
-#  x >= -5.0                                    <- lower-bound on x
[…]

### 2023-10-11 examples/ex5.jl

@@ -1,0 +1,35 @@
+# https://arxiv.org/pdf/2303.04375.pdf
+
+using JuMP
+using DisjunctiveProgramming
+
+##
+m = GDPModel()
+@variable(m, 1 ≤ x[1:2] ≤ 9)
+@variable(m, Y[1:2], LogicalVariable)
+@variable(m, W[1:2], LogicalVariable)
+@objective(m, Max, sum(x))
+@constraint(m, y1[i=1:2], [1,4][i] ≤ x[i] ≤ [3,6][i], DisjunctConstraint(Y[1]))
+@constraint(m, w1[i=1:2], [1,5][i] ≤ x[i] ≤ [2,6][i], DisjunctConstraint(W[1]))
+@constraint(m, w2[i=1:2], [2,4][i] ≤ x[i] ≤ [3,5][i], DisjunctConstraint(W[2]))
+@constraint(m, y2[i=1:2], [8,1][i] ≤ x[i] ≤ [9,2][i], DisjunctConstraint(Y[2]))
+@disjunction(m, inner, [W[1], W[2]], DisjunctConstraint(Y[1]))
+@disjunction(m, outer, [Y[1], Y[2]])
+@constraint(m, Y in Exactly(1))
+@constraint(m, W in Exactly(Y[1]))
+
+##
+reformulate_model(m, BigM())
+print(m)
+
+##
+reformulate_model(m, Hull())
+print(m)
+
+##
+using Polyhedra, CDDLib, Plots
+relax_integrality(m)
+lib = CDDLib.Library(:exact)
+poly = polyhedron(vrep(polyhedron(m, lib)),lib)
+proj = project(poly,1:2)
+plot(proj, xlims = (0,10), ylims = (0,7), xticks = 0:10, yticks = 0:10)

### 2023-10-11 examples/ex6.jl

@@ -1,0 +1,60 @@
+using JuMP
+using DisjunctiveProgramming
+
+##
+m = GDPModel()
+@variable(m, -5 <= x[1:3] <= 5)
+
+@variable(m, y[1:2], LogicalVariable)
+@constraint(m, x[1] <= -2, DisjunctConstraint(y[1]))
+@constraint(m, x[1] >= 2, DisjunctConstraint(y[2]))
+@constraint(m, x[2] == -1, DisjunctConstraint(y[2]))
+@constraint(m, x[3] == 1, DisjunctConstraint(y[2]))
+@disjunction(m, y)
+@constraint(m, y in Exactly(1))
+
+@variable(m, w[1:2], LogicalVariable)
+@constraint(m, x[2] <= -3, DisjunctConstraint(w[1]))
+@constraint(m, x[2] >= 3, DisjunctConstraint(w[2]))
+@constraint(m, x[3] == 0, DisjunctConstraint(w[2]))
+@disjunction(m, w, DisjunctConstraint(y[1]))
+@constraint(m, w in Exactly(y[1]))
+
+@variable(m, z[1:2], LogicalVariable)
+@constraint(m, x[3] <= -4, DisjunctConstraint(z[1]))
+@constraint(m, x[3] >= 4, DisjunctConstraint(z[2]))
+@disjunction(m, z, DisjunctConstraint(w[1]))
+@constraint(m, z in Exactly(w[1]))
+
+##
+reformulate_model(m, BigM())
+print(m)
+# Feasibility
+# Subject to
+#  y[1] + y[2] = 1
+#  -y[1] + w[1] + w[2] = 0
+#  -w[1] + z[1] + z[2] = 0
+#  x[3] - 9 z[2] ≥ -5
+#  x[2] - 8 w[2] ≥ -5
+#  x[3] - 5 w[2] ≥ -5
+#  x[1] - 7 y[2] ≥ -5
+#  x[2] - 4 y[2] ≥ -5
+#  x[3] - 6 y[2] ≥ -5
+#  x[1] + 7 y[1] ≤ 5
+#  x[2] + 8 w[1] ≤ 5
+#  x[3] + 9 z[1] ≤ 5
+#  x[3] + 5 w[2] ≤ 5
+#  x[2] + 6 y[2] ≤ 5
+#  x[3] + 4 y[2] ≤ 5
+#  x[1] ≥ -5
[…]

### 2023-10-11 src/bigm.jl

@@ -1,81 +1,199 @@
-"""
-    big_m_reformulation!(constr::ConstraintRef, bin_var, M, i, j, k)
-
-Perform Big-M reformulation on a linear or quadratic constraint at index k of constraint j in disjunct i.
-
-    big_m_reformulation!(constr::NonlinearConstraintRef, bin_var, M, i, j, k)
-
-Perform Big-M reformulaiton on a nonlinear constraint at index k of constraint j in disjunct i.
-
-    big_m_reformulation!(constr::AbstractArray{<:ConstraintRef}, bin_var, M, i, j, k)
-
-Perform Big-M reformulation on a constraint at index k of constraint j in disjunct i.
-"""
-function big_m_reformulation!(constr::ConstraintRef, bin_var, M0, i, j, k)
-    M = get_reform_param(M0, i, j, k; constr)
-    if !ismissing(M0) && constraint_object(constr).set isa MOI.GreaterThan && M > 0
-        M = -M #if a positive bigM value was provided and constraint is GreaterThan, use the negative of this number (-M*(1-y) <= func)
+################################################################################
+#                              BIG-M VALUE
+################################################################################
+# Get Big-M value for a particular constraint
+function _get_M_value(func::JuMP.AbstractJuMPScalar, set::_MOI.AbstractSet, method::BigM)
+    if method.tighten
+        M = _get_tight_M(func, set, method)
+    else
+        M = _get_M(func, set, method)
     end
-    add_to_function_constant(constr, -M)
-    set_normalized_coefficient(constr, constr.model[bin_var][i], M)
-end
-function big_m_reformulation!(constr::NonlinearConstraintRef, bin_var, M0, i, j, k)
-    M = get_reform_param(M0, i, j, k; constr)
-    #create symbolic variables (using Symbolics.jl)
-    for var_ref in get_constraint_variables(constr)
-        symbolic_variable(var_ref)
-    end
-    bin_var_sym = Symbol("$bin_var[$i]")
-    λ = Num(Symbolics.Sym{Float64}(bin_var_sym))
-    
-    #parse constr
-    op, lhs, rhs = parse_constraint(constr)
-    replace_Symvars!(lhs, constr.model) #convert JuMP variables into Symbolic variables
[…]

### 2023-10-11 src/constraints.jl

@@ -1,0 +1,541 @@
+################################################################################
+#                         HELPER SET MAPPING FUNCTIONS
+################################################################################
+# helper functions to get the value of an MOI set
+_set_value(set::_MOI.LessThan) = set.upper
+_set_value(set::_MOI.GreaterThan) = set.lower
+_set_value(set::_MOI.EqualTo) = set.value
+_set_values(set::_MOI.EqualTo) = (set.value, set.value)
+_set_values(set::_MOI.Interval) = (set.lower, set.upper)
+
+# helper functions to reformulate vector constraints to indicator constraints
+_vec_to_scalar_set(set::_MOI.Nonpositives) = _MOI.LessThan(0)
+_vec_to_scalar_set(set::_MOI.Nonnegatives) = _MOI.GreaterThan(0)
+_vec_to_scalar_set(set::_MOI.Zeros) = _MOI.EqualTo(0)
+
+# helper functions to map jump selector to moi selector sets
+_jump_to_moi_selector(set::Exactly) = _MOIExactly
+_jump_to_moi_selector(set::AtLeast) = _MOIAtLeast
+_jump_to_moi_selector(set::AtMost) = _MOIAtMost
+
+# helper functions to map selectors to scalar sets
+_vec_to_scalar_set(set::_MOIExactly) = _MOI.EqualTo
+_vec_to_scalar_set(set::_MOIAtLeast) = _MOI.GreaterThan
+_vec_to_scalar_set(set::_MOIAtMost) = _MOI.LessThan
+
+################################################################################
+#                         BOILERPLATE EXTENSION METHODS
+################################################################################
+for (RefType, loc) in ((:DisjunctConstraintRef, :disjunct_constraints), 
+                       (:DisjunctionRef, :disjunctions), 
+                       (:LogicalConstraintRef, :logical_constraints))
+    @eval begin
+        @doc """
+            JuMP.owner_model(cref::$($RefType))
+
+        Return the model to which `cref` belongs.
+        """
+        JuMP.owner_model(cref::$RefType) = cref.model
+
+        @doc """
+            JuMP.index(cref::$($RefType))
+
+        Return the index constraint associated with `cref`.
+        """
+        JuMP.index(cref::$RefType) = cref.index
+
+        @doc """
+            JuMP.is_valid(model::JuMP.Model, cref::$($RefType))
+
+        Return `true` if `cref` refers to a valid constraint in the `GDP model`.
+        """
[…]

### 2023-10-11 src/indicator.jl

@@ -1,0 +1,35 @@
+################################################################################
+#                              INDICATOR REFORMULATION
+################################################################################
+#scalar disjunct constraint
+function reformulate_disjunct_constraint(
+    model::JuMP.Model,
+    con::JuMP.ScalarConstraint{T, S},
+    bvref::JuMP.VariableRef,
+    method::Indicator
+) where {T, S}
+    reform_con = JuMP.build_constraint(error, [1*bvref, con.func], _MOI.Indicator{_MOI.ACTIVATE_ON_ONE}(con.set))
+    return [reform_con]
+end
+#vectorized disjunct constraint
+function reformulate_disjunct_constraint(
+    model::JuMP.Model,
+    con::JuMP.VectorConstraint{T, S},
+    bvref::JuMP.VariableRef,
+    method::Indicator
+) where {T, S}
+    set = _vec_to_scalar_set(con.set)
+    return [
+        JuMP.build_constraint(error, [1*bvref, f], _MOI.Indicator{_MOI.ACTIVATE_ON_ONE}(set)) 
+        for f in con.func
+    ]
+end
+#nested indicator reformulation. NOTE: the user needs to provide the appropriate linking constraint for the logical variables for this to work (e.g. w in Exactly(y[1]) to link the parent disjunct y[1] to the nested disjunction w)
+function reformulate_disjunct_constraint(
+    model::JuMP.Model,
+    con::JuMP.VectorConstraint{T, S},
+    bvref::JuMP.VariableRef,
+    method::Indicator
+) where {T, S <: _MOI.Indicator}
+    return [con]
+end

### 2023-10-11 src/logic.jl

@@ -1,59 +1,31 @@
-"""
-    choose!(m::Model, n::Union{Int,VariableRef}, vars::VariableRef...; mode::Symbol=:exactly, name::String="")
-
-Add constraint to select n elements from the list of variables. Options for mode
-are `:at_least`, `:at_most`, `:exactly`. Alternately, if `n` is a Binary variable, 
-it becomes the RHS of the constraint. If `name` is provided, it will be converted 
-to a Symbol and stored in the object dictionary.
-"""
-function choose!(m::Model, n::Int, vars::VariableRef...; mode::Symbol=:exactly, name::String="")
-    @assert length(vars) >= n "Not enough variables passed."
-    @assert all(is_valid.(m, vars)) "Invalid VariableRefs passed."
-    add_selection!(m, n, vars...; mode, name)
-end
-function choose!(m::Model, var::VariableRef, vars::VariableRef...; mode::Symbol=:exactly, name::String="")
-    @assert all(is_valid.(m, vcat(var,vars...))) "Invalid VariableRefs passed."
-    add_selection!(m, var, vars...; mode, name)
-end
-function add_selection!(m::Model, n, vars::VariableRef...; mode::Symbol, name::String)
-    if mode == :exactly
-        con = @constraint(m, sum(vars) == n)
-    elseif mode == :at_least
-        con = @constraint(m, sum(vars) ≥ n)
-    elseif mode == :at_most
-        con = @constraint(m, sum(vars) ≤ n)
-    end
-    if !isempty(name)
-        set_name(con, name)
-        m[Symbol(name)] = con
-    end
+################################################################################
+#                              LOGIC OPERATORS
+################################################################################
+function _op_fallback(name)
+    error("`$name` is only supported for logical expressions")
 end
 
-"""
-    add_proposition!(m::Model, expr::Expr; name::String = "")
-
-Convert logical proposition expression into conjunctive normal form.
-"""
-function add_proposition!(m::Model, expr::Expr; name::String = "")
-    if isempty(name)
-        name = "{$expr}" #get name to register reformulated logical proposition
+# Define all the logical operators
+const _LogicalOperatorHeads = (:(==), :(=>), :||, :&&, :!)
+for (name, alt, head) in (
+    (:⇔, :iff, :(==)), # \Leftrightarrow + tab
[…]

### 2023-10-11 src/macros.jl

@@ -1,125 +1,358 @@
-"""
-    disjunction(m, args...)
-
-Add disjunction macro.
-"""
-macro disjunction(m, args...)
-    #get disjunction (args) and keyword arguments
-    disjuncts, kwargs, _ = Containers._extract_kw_args(args)
-
-    #get kwargs and set defaults if missing
-    reformulation_kwarg = filter(i -> i.args[1] == :reformulation, kwargs)
-    reformulation = isempty(reformulation_kwarg) ? throw(UndefKeywordError(:reformulation)) : reformulation_kwarg[1].args[2]
-    M_kwarg = filter(i -> i.args[1] == :M, kwargs)
-    M = isempty(M_kwarg) ? :missing : M_kwarg[1].args[2]
-    ϵ_kwarg = filter(i -> i.args[1] == :ϵ, kwargs)
-    ϵ = isempty(ϵ_kwarg) ? :(1e-6) : ϵ_kwarg[1].args[2]
-    name_kwarg = filter(i -> i.args[1] == :name, kwargs)
-    name = isempty(name_kwarg) ? Symbol("disj_",gensym()) : name_kwarg[1].args[2]
-    disj_name = isempty(name_kwarg) ? name : Symbol("disj_",eval(name))
-    
-    #create constraints for each disjunction
-    disj_names = [Symbol("$(disj_name)[$i]") for i in eachindex(disjuncts)]
-    disjunction = []
-    for (d,dname) in zip(disjuncts,disj_names)
-        if Meta.isexpr(d, :tuple)
-            for (j,di) in enumerate(d.args)
-                i = findfirst(x -> x == d, disjuncts)
-                dname_j = Symbol("$(disj_name)[$i,$j]")
-                d.args[j] = add_disjunction_constraint(m, di, dname_j)
-            end
-            push!(disjunction, d)
-        else
-            push!(disjunction, add_disjunction_constraint(m, d, dname))
-        end
-    end
-    
-    #build disjunction
-    code = quote
-        DisjunctiveProgramming.add_disjunction!($m, $(disjunction...); reformulation = $reformulation, M = $M, ϵ = $ϵ, name = $name)
-    end
-
-    return esc(code)
+################################################################################
+#                                BASIC HELPERS
+################################################################################
+# Macro error function
+# inspired from https://github.com/jump-dev/JuMP.jl/blob/709d41b78e56efb4f2c54414266b30932010bd5a/src/macros.jl#L923-L928
+function _macro_error(macroname, args, source, str...)
[…]

### 2023-10-11 src/model.jl

@@ -1,0 +1,84 @@
+################################################################################
+#                              GDP MODEL
+################################################################################
+
+"""
+    GDPModel([optimizer]; [kwargs...])::JuMP.Model
+
+The core model object for building general disjunction programming models.
+"""
+function GDPModel(args...; kwargs...)
+    model = JuMP.Model(args...; kwargs...)
+    model.ext[:GDP] = GDPData()
+    JuMP.set_optimize_hook(model, _optimize_hook)
+    return model
+end
+
+# Define what should happen to solve a GDPModel
+# See https://github.com/jump-dev/JuMP.jl/blob/9ea1df38fd320f864ab4c93c78631d0f15939c0b/src/JuMP.jl#L718-L745
+function _optimize_hook(
+    model::JuMP.Model; 
+    method::AbstractSolutionMethod
+    ) # can add more kwargs if wanted
+    if !_ready_to_optimize(model) || _solution_method(model) != method
+        reformulate_model(model, method)
+    end
+    return JuMP.optimize!(model; ignore_optimize_hook = true)
+end
+
+################################################################################
+#                              GDP DATA
+################################################################################
+
+"""
+    gdp_data(model::JuMP.Model)::GDPData
+
+Extract the [`GDPData`](@ref) from a `GDPModel`.
+"""
+function gdp_data(model::JuMP.Model)
+    is_gdp_model(model) || error("Cannot access GDP data from a regular `JuMP.Model`.")
+    return model.ext[:GDP]
+end
+
+"""
+    is_gdp_model(model::JuMP.Model)::Bool
+
+Return if `model` was created via the [`GDPModel`](@ref) constructor.
+"""
+function is_gdp_model(model::JuMP.Model)
+    return haskey(model.ext, :GDP)
+end
+
+"""
+    disjunction_indicators(disjunction::DisjunctionRef) 
+
+Return LogicalVariableRefs associated with a disjunction.
+"""
+function disjunction_indicators(disjunction::DisjunctionRef) 
+    model, idx = disjunction.model, disjunction.index
+    return _disjunctions(model)[idx].constraint.indicators
+end
+
+# Create accessors for GDP data fields
+_logical_variables(model::JuMP.Model) = gdp_data(model).logical_variables
+_logical_constraints(model::JuMP.Model) = gdp_data(model).logical_constraints
[…]

### 2023-10-11 src/reformulate.jl

@@ -1,69 +1,169 @@
+################################################################################
+#                              REFORMULATE
+################################################################################
 """
-    reformulate_disjunction(m::Model, disj...; bin_var, reformulation, param)
+    reformulate_model(model::JuMP.Model, method::AbstractSolutionMethod)
 
-Reformulate disjunction on a JuMP model.
-
-    reformulate_disjunction(disj, bin_var, reformulation, param)
-
-Reformulate disjunction.
+Reformulate a `GDPModel` using the specified `method`. Prior to reformulation,
+all previous reformulation variables and constraints are deleted.
 """
-function reformulate_disjunction(m::Model, disj...; bin_var, reformulation, param)
-    #placeholder to store new constraints (reformulated)
-    @assert !in(bin_var, keys(m.ext)) "$bin_var cannot be used as the indicator variable for the disjunction because it has already been used on another disjunction."
-    m.ext[bin_var] = [] #store constraints associated with indicator variable
-    #check disj
-    disj = [check_constraint!(m, constr) for constr in disj]
-    #run reformulation
-    if reformulation == :hull
-        if !in(:disaggregated_variables, keys(m.ext))
-            m.ext[:disaggregated_variables] = Dict{String,VariableRef}() #record disaggregated variables to avoid duplicating disaggregation (nested disjunctions)
+function reformulate_model(model::JuMP.Model, method::AbstractSolutionMethod)
+    #clear all previous reformulations
+    _clear_reformulations(model)
+    #reformulate
+    _reformulate_logical_variables(model)
+    _reformulate_disjunctions(model, method)
+    _reformulate_logical_constraints(model)
+    #set solution method
+    _set_solution_method(model, method)
+    _set_ready_to_optimize(model, true)
+end
+
+function _clear_reformulations(model::JuMP.Model)
+    JuMP.delete.(model, _reformulation_constraints(model))
+    JuMP.delete.(model, _reformulation_variables(model))
+    empty!(gdp_data(model).reformulation_constraints)
+    empty!(gdp_data(model).reformulation_variables)
+end
+
+################################################################################
+#                              LOGICAL VARIABLES
+################################################################################
+# create binary (indicator) variables for logic variables.
[…]

### 2023-10-11 test/aqua.jl

@@ -1,0 +1,5 @@
+using Aqua
+using DisjunctiveProgramming
+
+Aqua.test_all(DisjunctiveProgramming, ambiguities = false)
+Aqua.test_ambiguities(DisjunctiveProgramming)

### 2023-10-11 test/constraints/proposition.jl

@@ -1,0 +1,531 @@
+function test_proposition_add_fail()
+    m = GDPModel()
+    @variable(m, y[1:3], LogicalVariable)
+    @test_throws ErrorException @constraint(Model(), logical_or(y...) in IsTrue())
+    @test_throws ErrorException @constraint(m, logical_or(y...) == 2)
+    @test_throws ErrorException @constraint(m, logical_or(y...) <= 1)
+    @test_throws ErrorException @constraint(m, sum(y) in IsTrue())
+    @test_throws ErrorException @constraint(m, prod(y) in IsTrue())
+    @test_throws ErrorException @constraint(m, sin(y[1]) in IsTrue())
+    @test_throws MethodError @constraint(m, logical_or(y...) == IsTrue())
+    @test_throws AssertionError @constraint(GDPModel(), logical_or(y...) in IsTrue())
+end
+
+function test_negation_add_success()
+    model = GDPModel()
+    @variable(model, y, LogicalVariable)
+    c1 = @constraint(model, logical_not(y) in IsTrue())
+    @constraint(model, c2, ¬y in IsTrue())
+    @test is_valid(model, c1)
+    @test is_valid(model, c2)
+    @test owner_model(c1) == model
+    @test owner_model(c2) == model
+    @test name(c1) == ""
+    @test name(c2) == "c2"
+    @test index(c1) == LogicalConstraintIndex(1)
+    @test index(c2) == LogicalConstraintIndex(2)
+    @test haskey(DP._logical_constraints(model), index(c1))
+    @test haskey(DP._logical_constraints(model), index(c2))
+    @test DP._logical_constraints(model)[index(c1)] == DP._constraint_data(c1)
+    @test constraint_object(c1).func isa DP._LogicalExpr
+    @test constraint_object(c2).func isa DP._LogicalExpr
+    @test constraint_object(c1).func.head == 
+            constraint_object(c2).func.head == :!
+    @test constraint_object(c1).func.args ==
+            constraint_object(c2).func.args == Any[y]
+    @test constraint_object(c1).set == 
+            constraint_object(c2).set == IsTrue()
+    @test c1 == copy(c1)
+end
+
+function test_implication_add_success()
+    model = GDPModel()
+    @variable(model, y[1:2], LogicalVariable)
+    @constraint(model, c1, implies(y...) in IsTrue())
[…]

### 2023-10-11 test/disjunction.jl

@@ -1,0 +1,216 @@
+function test_disjunction_add_fail()
+    model = GDPModel()
+    @variable(model, x)
+    @variable(model, y[1:2], LogicalVariable)
+    @constraint(model, x == 5, DisjunctConstraint(y[1]))
+
+    @test_macro_throws ErrorException @disjunction(model) #not enough arguments
+    @test_macro_throws UndefVarError @disjunction(model, y) #unassociated indicator
+    @test_macro_throws UndefVarError @disjunction(GDPModel(), y) #wrong model
+    @test_macro_throws ErrorException @disjunction(Model(), y) #not a GDPModel
+    @test_macro_throws UndefVarError @disjunction(model, [y[1], y[1]]) #duplicate indicator
+    @test_macro_throws UndefVarError @disjunction(model, y[1]) #no disjunction expression
+    @test_macro_throws UndefVarError @disjunction(model, y, "random_arg") #unrecognized extra argument
+    @test_macro_throws ErrorException @disjunction(model, "ABC") #unrecognized structure
+    @test_macro_throws ErrorException @disjunction(model, begin y end) #@disjunctions (plural)
+    @test_macro_throws UndefVarError @disjunction(model, x, y) #name x already exists
+
+    @constraint(model, x == 10, DisjunctConstraint(y[2]))
+    @disjunction(model, disj, y)
+    @test_macro_throws UndefVarError @disjunction(model, disj, y) #duplicate name
+
+    @test_macro_throws ErrorException @disjunction(model, "bad"[i=1:2], y) #wrong expression for disjunction name
+    @test_macro_throws ErrorException @disjunction(model, [model=1:2], y) #index name can't be same as model name
+end
+
+function test_disjunction_add_success()
+    model = GDPModel()
+    @variable(model, x)
+    @variable(model, y[1:2], LogicalVariable)
+    @constraint(model, x == 5, DisjunctConstraint(y[1]))
+    @constraint(model, x == 10, DisjunctConstraint(y[2]))
+    disj = @disjunction(model, y)
+    @disjunction(model, disj2, y)
+    @test owner_model(disj) == model
+    @test is_valid(model, disj)
+    @test index(disj) == DisjunctionIndex(1)
+    @test name(disj) == ""
+    @test name(disj2) == "disj2"
[…]

### 2023-10-11 test/model.jl

@@ -1,0 +1,39 @@
+using HiGHS
+
+function test_empty_model()
+    model = GDPModel()
+    @test gdp_data(model) isa GDPData
+    @test isempty(DP._logical_variables(model))
+    @test isempty(DP._logical_constraints(model))
+    @test isempty(DP._disjunct_constraints(model))
+    @test isempty(DP._disjunctions(model))
+    @test isempty(DP._indicator_to_binary(model))
+    @test isempty(DP._indicator_to_constraints(model))
+    @test isempty(DP._reformulation_variables(model))
+    @test isempty(DP._reformulation_constraints(model))
+    @test isnothing(DP._solution_method(model))
+    @test !DP._ready_to_optimize(model)
+end
+
+function test_non_gdp_model()
+    model = Model()
+    @test_throws ErrorException gdp_data(model)
+end
+
+function test_creation_optimizer()
+    model = GDPModel(HiGHS.Optimizer)
+    @test solver_name(model) == "HiGHS"
+end
+
+function test_set_optimizer()
+    model = GDPModel()
+    set_optimizer(model, HiGHS.Optimizer)
+    @test solver_name(model) == "HiGHS"
+end
+
+@testset "GDP Model" begin
+    test_empty_model()
+    test_non_gdp_model()
+    test_creation_optimizer()
+    test_set_optimizer()
+end

### 2023-10-11 test/runtests.jl

@@ -1,0 +1,40 @@
+using DisjunctiveProgramming
+using JuMP
+using Test
+
+const DP = DisjunctiveProgramming
+
+struct DummyReformulation <: AbstractReformulationMethod end
+
+# Utilities to test macro error exception
+# Taken from https://github.com/jump-dev/JuMP.jl/blob/master/test/utilities.jl
+function strip_line_from_error(err::ErrorException)
+    return ErrorException(replace(err.msg, r"^At.+\:[0-9]+\: `@" => "In `@"))
+end
+strip_line_from_error(err::LoadError) = strip_line_from_error(err.error)
+strip_line_from_error(err) = err
+macro test_macro_throws(errortype, m)
+    quote
+        @test_throws(
+            $(esc(strip_line_from_error(errortype))),
+            try
+                @eval $m
+            catch err
+                throw(strip_line_from_error(err))
+            end
+        )
+    end
+end
+
+include("aqua.jl")
+include("model.jl")
+include("variables/query.jl")
+include("variables/logical.jl")
+include("constraints/selector.jl")
+include("constraints/proposition.jl")
+include("constraints/disjunct.jl")
+include("constraints/indicator.jl")
+include("constraints/bigm.jl")
+include("constraints/hull.jl")
+include("disjunction.jl")
+include("solve.jl")

### 2023-10-11 test/solve.jl

@@ -1,0 +1,50 @@
+using HiGHS
+
+function test_linear_gdp_example()
+    m = GDPModel(HiGHS.Optimizer)
+    set_attribute(m, MOI.Silent(), true)
+    @variable(m, 1 ≤ x[1:2] ≤ 9)
+    @variable(m, Y[1:2], LogicalVariable)
+    @variable(m, W[1:2], LogicalVariable)
+    @objective(m, Max, sum(x))
+    @constraint(m, y1[i=1:2], [1,4][i] ≤ x[i] ≤ [3,6][i], DisjunctConstraint(Y[1]))
+    @constraint(m, w1[i=1:2], [1,5][i] ≤ x[i] ≤ [2,6][i], DisjunctConstraint(W[1]))
+    @constraint(m, w2[i=1:2], [2,4][i] ≤ x[i] ≤ [3,5][i], DisjunctConstraint(W[2]))
+    @constraint(m, y2[i=1:2], [8,1][i] ≤ x[i] ≤ [9,2][i], DisjunctConstraint(Y[2]))
+    @disjunction(m, inner, [W[1], W[2]], DisjunctConstraint(Y[1]))
+    @disjunction(m, outer, [Y[1], Y[2]])
+    @constraint(m, Y in Exactly(1))
+    @constraint(m, W in Exactly(Y[1]))
+
+    optimize!(m, method = BigM())
+    @test termination_status(m) == MOI.OPTIMAL
+    @test objective_value(m) ≈ 11
+    @test value.(x) ≈ [9,2]
+    bins = gdp_data(m).indicator_to_binary
+    @test value(bins[Y[1]]) ≈ 0
+    @test value(bins[Y[2]]) ≈ 1
+    @test value(bins[W[1]]) ≈ 0
+    @test value(bins[W[2]]) ≈ 0
+
+    optimize!(m, method = Hull())
+    @test termination_status(m) == MOI.OPTIMAL
+    @test objective_value(m) ≈ 11
+    @test value.(x) ≈ [9,2]
+    bins = gdp_data(m).indicator_to_binary
+    @test value(bins[Y[1]]) ≈ 0
+    @test value(bins[Y[2]]) ≈ 1
+    @test value(bins[W[1]]) ≈ 0
+    @test value(bins[W[2]]) ≈ 0
+    @test value(variable_by_name(m, "x[1]_Y[1]")) ≈ 0
[…]

### 2023-10-11 test/variables/logical.jl

@@ -1,0 +1,168 @@
+# test creating, modifying, and reformulating logical variables
+function test_lvar_add_fail()
+   model = Model()
+   @test_throws ErrorException @variable(model, y, LogicalVariable)
+end
+
+function test_lvar_add_success()
+    model = GDPModel()
+    @variable(model, y, LogicalVariable)
+    @test typeof(y) == LogicalVariableRef
+    @test owner_model(y) == model
+    @test is_valid(model, y)
+    @test name(y) == "y"
+    @test index(y) == LogicalVariableIndex(1)
+    @test isnothing(start_value(y))
+    @test isnothing(fix_value(y))
+    @test isequal_canonical(y, copy(y))
+    @test haskey(DP._logical_variables(model), index(y))
+    @test DP._logical_variables(model)[index(y)].variable == LogicalVariable(nothing, nothing)
+    @test DP._logical_variables(model)[index(y)].name == "y"
+    #reformulate the variable
+    test_lvar_reformulation(model, y)
+end
+
+function test_lvar_add_array()
+    model = GDPModel()
+    @variable(model, y[1:3, 1:2], LogicalVariable)
+    @test y isa Array{LogicalVariableRef, 2}
+    @test length(y) == 6
+end
+
+function test_lvar_add_dense_axis()
+    model = GDPModel()
+    @variable(model, y[["a","b","c"],[1,2]], LogicalVariable)
+    @test y isa Containers.DenseAxisArray
+    @test length(y) == 6
+    @test y.axes[1] == ["a","b","c"]
+    @test y.axes[2] == [1,2]
+    @test y.data isa Array{LogicalVariableRef, 2}
+end
+
+function test_lvar_add_sparse_axis()
+    model = GDPModel()
+    @variable(model, y[i = 1:3, j = 1:3; j > i], LogicalVariable)
+    @test y isa Containers.SparseAxisArray
+    @test length(y) == 3
+    @test y.names == (:i, :j)
+    @test Set(keys(y.data)) == Set([(1,2),(1,3),(2,3)])
+end
+
+function test_lvar_set_name()
+    model = GDPModel()
+    @variable(model, y, LogicalVariable)
+    set_name(y, "z")
+    @test name(y) == "z"
+    #reformulate the variable
+    test_lvar_reformulation(model, y)
+end
+
+function test_lvar_creation_start_value()
+    model = GDPModel()
+    @variable(model, y, LogicalVariable, start = true)
+    @test start_value(y)
+    #reformulate the variable
[…]

### 2023-10-11 test/variables/query.jl

@@ -1,0 +1,168 @@
+function test_interrogate_non_variables()
+    vars = Set()
+    f = Base.Fix1(push!, vars) #interrogator
+    #numbers
+    DP._interrogate_variables(f, 1)
+    @test isempty(vars)
+    empty!(vars)
+    DP._interrogate_variables(f, 1.0)
+    @test isempty(vars)
+    empty!(vars)
+    #strings/symbols
+    @test_throws ErrorException DP._interrogate_variables(f, "a")
+    @test_throws ErrorException DP._interrogate_variables(f, :a)
+end
+
+function test_interrogate_variables()
+    vars = Set()
+    f = Base.Fix1(push!, vars) #interrogator
+    m = GDPModel()
+    @variable(m, x)
+    @variable(m, y, LogicalVariable)
+    DP._interrogate_variables(f, [x, y])
+    @test x in vars
+    @test y in vars
+    @test length(vars) == 2
+end
+
+function test_interrogate_affexpr()
+    vars = Set()
+    f = Base.Fix1(push!, vars) #interrogator
+    m = GDPModel()
+    @variable(m, x)
+    @variable(m, y, LogicalVariable)
+    @variable(m, z)
+    DP._interrogate_variables(f, x + y + z)
+    @test x in vars
+    @test y in vars
+    @test z in vars
+    @test length(vars) == 3
+end
+
+function test_interrogate_quadexpr()
+    vars = Set()
+    f = Base.Fix1(push!, vars) #interrogator
+    m = GDPModel()
+    @variable(m, x)
+    @variable(m, y, LogicalVariable)
+    @variable(m, z)
+    DP._interrogate_variables(f, x^2 + x*y + z + 1)
+    @test x in vars
+    @test y in vars
+    @test z in vars
+    @test length(vars) == 3
+    empty!(vars)
+end
+
+function test_interrogate_nonlinear_expr()
+    vars = Set()
+    f = Base.Fix1(push!, vars) #interrogator
+    m = GDPModel()
+    @variable(m, x)
+    @variable(m, y, LogicalVariable)
+    @variable(m, z)
+    DP._interrogate_variables(f, sin(exp(x^2 + 1)) + cos(x) + y + 2)
+    @test x in vars
+    @test y in vars
+    @test !(z in vars)
+    @test length(vars) == 2
+end
+
[…]

### 2023-10-12 src/datatypes.jl
initial commit

@@ -373,6 +373,33 @@ A type for using indicator constraint approach for linear disjunctive constraint
 """
 struct Indicator <: AbstractReformulationMethod end
 
+"""
+    MOIDisjunction <: AbstractReformulationMethod
+A reformulation type for reformulating disjunctions into their MathOptInterface 
+set representations [`DisjucntionSet`](@ref) which are then added to the model.
+"""
+struct MOIDisjunction <: AbstractReformulationMethod end
+
+"""
+    DisjunctionSet{S <: MOI.AbstractSet} <: MOI.AbstractVectorSet
+A MathOptInterface set for representing disjunctions in the format vector of 
+functions in set to enable:
+```julia
+@constraint(model, [funcs...] in DisjunctionSet(n, idxs, sets))
+```
+where the vector of functions `funcs` is a flattened version of all the disjunct 
+constraint functions where the indicator variable is listed first, `n` is the 
+length of `[funcs...]`, `idxs` is a vector of the indices tracking where each 
+disjunct begins (i.e., it stores the indices of the indicator variables in 
+`[funcs...]`), and `sets` is a uses a vector of vectors structure for the MOI sets 
+that correspond to all the disjunct constraint functions.
+"""
+struct DisjunctionSet{S <: _MOI.AbstractSet} <: _MOI.AbstractVectorSet 
+    dimension::Int
+    disjunct_indices::Vector{Int}
+    constraint_sets::Vector{Vector{S}}
+end
+
 ################################################################################
 #                              GDP Data
 ################################################################################

### 2023-10-12 src/moi.jl

@@ -1,0 +1,58 @@
+################################################################################
+#                               UTILITY METHODS
+################################################################################
+# Requred for extensions to MOI.AbstractVectorSet
+# function _MOI.Utilities.set_dot(x::AbstractVector, y::AbstractVector, set::DisjunctionSet)
+#     return LinearAlgebra.dot(x, y) # TODO figure out what we should actually do here
+# end
+
+# TODO create a bridge for `DisjunctionSet`
+
+# TODO create helper method to unpack DisjunctionSet at the MOI side of things
+
+################################################################################
+#                            REFRORMULATION METHODS
+################################################################################
+# Helper methods to handle recursively flattening the disjuncts
+function _constr_set!(funcs, con::JuMP.AbstractConstraint)
+    append!(funcs, JuMP.jump_function(con))
+    return JuMP.moi_set(con)
+end
+function _constr_set!(funcs, con::Disjunction)
+    inner_funcs, set = _disjunction_to_set(con)
+    append!(funcs, inner_funcs)
+    return set
+end
+
+# Create the vectors needed for a disjunction vector constraint
+function _disjunction_to_set(d::Disjunction)
+    # allocate memory for the storage vectors
+    num_disjuncts = length(d.indicators)
+    funcs = sizehint!(JuMP.AbstractJuMPScalar[], num_disjuncts)
+    sets = Vector{Vector{_MOI.AbstractSet}}(undef, num_disjuncts)
+    d_idxs = Vector{Int}(undef, num_disjuncts)
+    # iterate over the underlying disjuncts to fill in the storage vectors
+    for (i, lvref) in enumerate(d.indicators)
+        model = JuMP.owner_model(lvref)
+        push!(funcs, _indicator_to_binary(model)[lvref])
+        d_idxs[i] = length(funcs)
+        crefs = _indicator_to_constraints(model)[lvref]
+        sets[i] = map(c -> _constr_set!(funcs, JuMP.constraint_object(c)), crefs)
+    end
+    # convert the `sets` type to be concrete if possible (TODO benchmark if this is worth it)
+    SetType = typeof(first(sets))
+    if SetType != Vector{_MOI.AbstractSet} && all(s -> s isa SetType, sets) 
+        sets = convert(SetType, sets)
+    end
+    return funcs, DisjunctionSet(length(funcs), d_idxs, sets)
+end
+
+# Extend the disjunction reformulation
[…]

### 2023-10-12 src/moi.jl
Improve allocation

@@ -14,30 +14,31 @@
 #                            REFRORMULATION METHODS
 ################################################################################
 # Helper methods to handle recursively flattening the disjuncts
-function _constr_set!(funcs, con::JuMP.AbstractConstraint)
+function _constr_set!(model, funcs, con::JuMP.AbstractConstraint)
     append!(funcs, JuMP.jump_function(con))
     return JuMP.moi_set(con)
 end
-function _constr_set!(funcs, con::Disjunction)
-    inner_funcs, set = _disjunction_to_set(con)
+function _constr_set!(model, funcs, con::Disjunction)
+    inner_funcs, set = _disjunction_to_set(model, con)
     append!(funcs, inner_funcs)
     return set
 end
 
 # Create the vectors needed for a disjunction vector constraint
-function _disjunction_to_set(d::Disjunction)
+function _disjunction_to_set(model::JuMP.Model, d::Disjunction)
     # allocate memory for the storage vectors
     num_disjuncts = length(d.indicators)
-    funcs = sizehint!(JuMP.AbstractJuMPScalar[], num_disjuncts)
+    constr_mappings = _indicator_to_constraints(model)
+    num_constrs = sum(length(constr_mappings[lvref]) for lvref in d.indicators)
+    funcs = sizehint!(JuMP.AbstractJuMPScalar[], num_disjuncts + num_constrs)
     sets = Vector{Vector{_MOI.AbstractSet}}(undef, num_disjuncts)
     d_idxs = Vector{Int}(undef, num_disjuncts)
     # iterate over the underlying disjuncts to fill in the storage vectors
     for (i, lvref) in enumerate(d.indicators)
-        model = JuMP.owner_model(lvref)
         push!(funcs, _indicator_to_binary(model)[lvref])
         d_idxs[i] = length(funcs)
-        crefs = _indicator_to_constraints(model)[lvref]
-        sets[i] = map(c -> _constr_set!(funcs, JuMP.constraint_object(c)), crefs)
+        crefs = constr_mappings(model)[lvref]
+        sets[i] = map(c -> _constr_set!(model, funcs, JuMP.constraint_object(c)), crefs)
     end
     # convert the `sets` type to be concrete if possible (TODO benchmark if this is worth it)
     SetType = typeof(first(sets))
@@ -53,6 +54,6 @@ function reformulate_disjunction(
     d::Disjunction, 
     ::MOIDisjunction
     )
[…]

### 2023-10-13 src/datatypes.jl
typo
Co-authored-by: David Bernal <dbernaln@purdue.edu>

@@ -376,7 +376,7 @@ struct Indicator <: AbstractReformulationMethod end
 """
     MOIDisjunction <: AbstractReformulationMethod
 A reformulation type for reformulating disjunctions into their MathOptInterface 
-set representations [`DisjucntionSet`](@ref) which are then added to the model.
+set representations [`DisjunctionSet`](@ref) which are then added to the model.
 """
 struct MOIDisjunction <: AbstractReformulationMethod end
 

### 2023-10-13 examples/ex2.jl
add Logical alias for Logical Variable. Closes #73

@@ -5,7 +5,7 @@ using HiGHS
 
 m = GDPModel(HiGHS.Optimizer)
 @variable(m, 0 ≤ x[1:2] ≤ 20)
-@variable(m, Y[1:2], LogicalVariable)
+@variable(m, Y[1:2], Logical)
 @constraint(m, [i = 1:2], [2,5][i] ≤ x[i] ≤ [6,9][i], DisjunctConstraint(Y[1]))
 @constraint(m, [i = 1:2], [8,10][i] ≤ x[i] ≤ [11,15][i], DisjunctConstraint(Y[2]))
 @disjunction(m, Y)

### 2023-10-13 examples/ex5.jl

@@ -6,8 +6,8 @@ using DisjunctiveProgramming
 ##
 m = GDPModel()
 @variable(m, 1 ≤ x[1:2] ≤ 9)
-@variable(m, Y[1:2], LogicalVariable)
-@variable(m, W[1:2], LogicalVariable)
+@variable(m, Y[1:2], Logical)
+@variable(m, W[1:2], Logical)
 @objective(m, Max, sum(x))
 @constraint(m, y1[i=1:2], [1,4][i] ≤ x[i] ≤ [3,6][i], DisjunctConstraint(Y[1]))
 @constraint(m, w1[i=1:2], [1,5][i] ≤ x[i] ≤ [2,6][i], DisjunctConstraint(W[1]))

### 2023-10-13 examples/ex6.jl

@@ -5,7 +5,7 @@ using DisjunctiveProgramming
 m = GDPModel()
 @variable(m, -5 <= x[1:3] <= 5)
 
-@variable(m, y[1:2], LogicalVariable)
+@variable(m, y[1:2], Logical)
 @constraint(m, x[1] <= -2, DisjunctConstraint(y[1]))
 @constraint(m, x[1] >= 2, DisjunctConstraint(y[2]))
 @constraint(m, x[2] == -1, DisjunctConstraint(y[2]))
@@ -13,14 +13,14 @@ m = GDPModel()
 @disjunction(m, y)
 @constraint(m, y in Exactly(1))
 
-@variable(m, w[1:2], LogicalVariable)
+@variable(m, w[1:2], Logical)
 @constraint(m, x[2] <= -3, DisjunctConstraint(w[1]))
 @constraint(m, x[2] >= 3, DisjunctConstraint(w[2]))
 @constraint(m, x[3] == 0, DisjunctConstraint(w[2]))
 @disjunction(m, w, DisjunctConstraint(y[1]))
 @constraint(m, w in Exactly(y[1]))
 
-@variable(m, z[1:2], LogicalVariable)
+@variable(m, z[1:2], Logical)
 @constraint(m, x[3] <= -4, DisjunctConstraint(z[1]))
 @constraint(m, x[3] >= 4, DisjunctConstraint(z[2]))
 @disjunction(m, z, DisjunctConstraint(w[1]))

### 2023-10-13 src/constraints.jl

@@ -419,7 +419,7 @@ To select exactly 1 logical variable `Y` to be `true`, do
 
 ```jldoctest
 julia> model = GDPModel();
-julia> @variable(model, Y[i = 1:2], LogicalVariable);
+julia> @variable(model, Y[i = 1:2], Logical);
 julia> @constraint(model, [Y[1], Y[2]] in Exactly(1));
 ```
 

### 2023-10-13 test/constraints/bigm.jl

@@ -19,7 +19,7 @@ end
 function test_get_M_1sided()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @constraint(model, con, 3*x <= 1, DisjunctConstraint(y))
     cobj = constraint_object(con)
     M = DP._get_M(cobj.func, cobj.set, BigM(100, false))
@@ -30,7 +30,7 @@ end
 function test_get_tight_M_1sided()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @constraint(model, con, 3*x <= 1, DisjunctConstraint(y))
     cobj = constraint_object(con)
 
@@ -53,7 +53,7 @@ end
 function test_get_M_2sided()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @constraint(model, con, 3*x == 1, DisjunctConstraint(y))
     cobj = constraint_object(con)
 
@@ -69,7 +69,7 @@ end
 function test_get_tight_M_2sided()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @constraint(model, con, 3*x == 1, DisjunctConstraint(y))
     cobj = constraint_object(con)
     
@@ -176,7 +176,7 @@ end
 function test_lessthan_bigm()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @constraint(model, con, x <= 5, DisjunctConstraint(y))
 
     DP._reformulate_logical_variables(model)
@@ -190,7 +190,7 @@ end
 function test_nonpositives_bigm()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @constraint(model, con, [x; x] <= [5; 5], DisjunctConstraint(y))
 
     DP._reformulate_logical_variables(model)
@@ -205,7 +205,7 @@ end
 function test_greaterhan_bigm()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @constraint(model, con, x >= 5, DisjunctConstraint(y))
 
[…]

### 2023-10-13 test/disjunction.jl

@@ -1,7 +1,7 @@
 function test_disjunction_add_fail()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y[1:2], LogicalVariable)
+    @variable(model, y[1:2], Logical)
     @constraint(model, x == 5, DisjunctConstraint(y[1]))
 
     @test_macro_throws ErrorException @disjunction(model) #not enough arguments
@@ -26,7 +26,7 @@ end
 function test_disjunction_add_success()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y[1:2], LogicalVariable)
+    @variable(model, y[1:2], Logical)
     @constraint(model, x == 5, DisjunctConstraint(y[1]))
     @constraint(model, x == 10, DisjunctConstraint(y[2]))
     disj = @disjunction(model, y)
@@ -47,8 +47,8 @@ end
 function test_disjunction_add_nested()
     model = GDPModel()
     @variable(model, x)
-    @variable(model, y[1:2], LogicalVariable)
-    @variable(model, z[1:2], LogicalVariable)
+    @variable(model, y[1:2], Logical)
+    @variable(model, z[1:2], Logical)
     @constraint(model, x <= 5, DisjunctConstraint(y[1]))
     @constraint(model, x >= 5, DisjunctConstraint(y[2]))
     @disjunction(model, inner, y, DisjunctConstraint(z[1]))
@@ -69,7 +69,7 @@ end
 function test_disjunction_add_array()
     model=GDPModel()
     @variable(model, x)
-    @variable(model, y[1:2, 1:3, 1:4], LogicalVariable)
+    @variable(model, y[1:2, 1:3, 1:4], Logical)
     @constraint(model, con[i=1:2, j=1:3, k=1:4], x==i+j+k, DisjunctConstraint(y[i,j,k]))
     @disjunction(model, disj[i=1:2, j=1:3], y[i,j,:])
 
@@ -83,7 +83,7 @@ function test_disjunciton_add_dense_axis()
     @variable(model, x)
     I = ["a", "b", "c"]
     J = [1, 2]
-    @variable(model, y[I, J, 1:4], LogicalVariable)
+    @variable(model, y[I, J, 1:4], Logical)
     @constraint(model, con[i=I, j=J, k=1:4], x==k, DisjunctConstraint(y[i,j,k]))
     @disjunction(model, disj[i=I, j=J], y[i,j,:])
 
@@ -96,7 +96,7 @@ end
[…]

### 2023-10-13 test/variables/logical.jl

@@ -1,12 +1,12 @@
 # test creating, modifying, and reformulating logical variables
 function test_lvar_add_fail()
    model = Model()
-   @test_throws ErrorException @variable(model, y, LogicalVariable)
+   @test_throws ErrorException @variable(model, y, Logical)
 end
 
 function test_lvar_add_success()
     model = GDPModel()
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     @test typeof(y) == LogicalVariableRef
     @test owner_model(y) == model
     @test is_valid(model, y)
@@ -24,14 +24,14 @@ end
 
 function test_lvar_add_array()
     model = GDPModel()
-    @variable(model, y[1:3, 1:2], LogicalVariable)
+    @variable(model, y[1:3, 1:2], Logical)
     @test y isa Array{LogicalVariableRef, 2}
     @test length(y) == 6
 end
 
 function test_lvar_add_dense_axis()
     model = GDPModel()
-    @variable(model, y[["a","b","c"],[1,2]], LogicalVariable)
+    @variable(model, y[["a","b","c"],[1,2]], Logical)
     @test y isa Containers.DenseAxisArray
     @test length(y) == 6
     @test y.axes[1] == ["a","b","c"]
@@ -41,7 +41,7 @@ end
 
 function test_lvar_add_sparse_axis()
     model = GDPModel()
-    @variable(model, y[i = 1:3, j = 1:3; j > i], LogicalVariable)
+    @variable(model, y[i = 1:3, j = 1:3; j > i], Logical)
     @test y isa Containers.SparseAxisArray
     @test length(y) == 3
     @test y.names == (:i, :j)
@@ -50,7 +50,7 @@ end
 
 function test_lvar_set_name()
     model = GDPModel()
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
     set_name(y, "z")
     @test name(y) == "z"
     #reformulate the variable
@@ -59,7 +59,7 @@ end
 
 function test_lvar_creation_start_value()
     model = GDPModel()
-    @variable(model, y, LogicalVariable, start = true)
+    @variable(model, y, Logical, start = true)
     @test start_value(y)
     #reformulate the variable
     test_lvar_reformulation(model, y)
@@ -67,7 +67,7 @@ end
 
 function test_lvar_set_start_value()
     model = GDPModel()
-    @variable(model, y, LogicalVariable)
+    @variable(model, y, Logical)
[…]

### 2023-10-13 docs/make.jl
remove using JuMP. remove jldoctests

@@ -1,12 +1,13 @@
-push!(LOAD_PATH,"../src/")
 using DisjunctiveProgramming
 using Documenter
 makedocs(
-         sitename = "DisjunctiveProgramming.jl",
-         modules  = [DisjunctiveProgramming],
-         pages=[
-                "Home" => "index.md"
-               ])
+    sitename = "DisjunctiveProgramming.jl",
+    modules  = [DisjunctiveProgramming],
+    pages=[
+        "Home" => "index.md"
+    ],
+    checkdocs = :none
+)
 deploydocs(;
     repo="github.com/hdavid16/DisjunctiveProgramming.jl",
 )

### 2023-10-13 examples/ex2.jl

@@ -1,5 +1,4 @@
 # https://optimization.cbe.cornell.edu/index.php?title=Disjunctive_inequalities#Big-M_Reformulation[1][2]
-using JuMP
 using DisjunctiveProgramming
 using HiGHS
 

### 2023-10-13 examples/ex3.jl

@@ -1,4 +1,3 @@
-using JuMP
 using DisjunctiveProgramming
 
 m = GDPModel()

### 2023-10-13 examples/ex4.jl

@@ -1,4 +1,3 @@
-using JuMP
 using DisjunctiveProgramming
 
 # Example with proposition reformulation

### 2023-10-13 examples/ex5.jl

@@ -1,6 +1,4 @@
 # https://arxiv.org/pdf/2303.04375.pdf
-
-using JuMP
 using DisjunctiveProgramming
 
 ##

### 2023-10-13 examples/ex6.jl

@@ -1,4 +1,3 @@
-using JuMP
 using DisjunctiveProgramming
 
 ##

### 2023-10-13 src/constraints.jl

@@ -417,10 +417,11 @@ cardinality sets: `AtLeast(n)`, `AtMost(n)`, or `Exactly(n)`.
 To select exactly 1 logical variable `Y` to be `true`, do 
 (the same can be done with `AtLeast(n)` and `AtMost(n)`):
 
-```jldoctest
-julia> model = GDPModel();
-julia> @variable(model, Y[i = 1:2], LogicalVariable);
-julia> @constraint(model, [Y[1], Y[2]] in Exactly(1));
+```julia
+using DisjunctiveProgramming
+model = GDPModel();
+@variable(model, Y[i = 1:2], LogicalVariable);
+@constraint(model, [Y[1], Y[2]] in Exactly(1));
 ```
 
     JuMP.build_constraint(

### 2023-10-13 src/macros.jl

@@ -285,23 +285,17 @@ The macro returns a tuple containing the disjunctions that were defined.
 
 ## Example
 
-```jldoctest
-julia> model = GDPModel();
-
-julia> @variable(model, w);
-
-julia> @variable(model, x);
-
-julia> @variable(model, Y[1:4], LogicalVariable);
-
-julia> @constraint(model, [i=1:2], w == i, DisjunctConstraint(Y[i]));
-
-julia> @constraint(model, [i=3:4], x == i, DisjunctConstraint(Y[i]));
-
-julia> @disjunctions(model, begin
-           [Y[1], Y[2]]
-           [Y[3], Y[4]]
-       end);
+```julia
+model = GDPModel();
+@variable(model, w);
+@variable(model, x);
+@variable(model, Y[1:4], LogicalVariable);
+@constraint(model, [i=1:2], w == i, DisjunctConstraint(Y[i]));
+@constraint(model, [i=3:4], x == i, DisjunctConstraint(Y[i]));
+@disjunctions(model, begin
+    [Y[1], Y[2]]
+    [Y[3], Y[4]]
+end);
 ````
 """
 macro disjunctions(m, x)

### 2023-10-13 test/runtests.jl

@@ -1,5 +1,4 @@
 using DisjunctiveProgramming
-using JuMP
 using Test
 
 const DP = DisjunctiveProgramming

### 2023-10-14 paper/paper.tex
fix #63
begin fixes to paper

@@
 
-\subsection{Linear GDP reformulation example}
+\subsection{Solution Technique: Reformulation to Mixed-Integer Program}
 The simplest example of a linear GDP system is given in \eqref{eq:ex} - \eqref{eq:y}, where $Y_i$ is a Boolean indicator variable that enforces the constraints in the disjunct ($Ax \le b$ or $Cx \le d$) when $true$.
@@
  \subsubsection{Big-M Reformulation}
- The Big-M reformulation for this problem is given by \eqref{eq:x}, \eqref{eq:ex_bigm1} - \eqref{eq:ex_bigm4}, where $M$ is a sufficiently large scalar that makes the particular constraint redundant when its indicator variable is not selected (i.e., $y_i = 0$).
+ The Big-M reformulation for this problem is given by \eqref{eq:ex_bigm1} - \eqref{eq:ex_bigm5}, where $M$ is a sufficiently large scalar that makes the particular constraint redundant when its indicator variable is not selected (i.e., $y_i = 0$).
 Note that the Boolean variables, $Y_i$, are replaced by binary variables, $y_i$.
@@
     \label{eq:ex_bigm4}
+    0 \leq x \leq U
+\end{equation}
+\begin{equation}
+    \label{eq:ex_bigm5}
     y_1, y_2 \in \{0,1\}
@@
 \subsubsection{Hull Reformulation}
-The Hull reformulation is given by \eqref{eq:x}, \eqref{eq:ex_bigm3} - \eqref{eq:ex_hull3}, which requires lifting the model to a higher-dimensional space.
+The Hull reformulation is given by \eqref{eq:ex_hull0} - \eqref{eq:ex_hull6}, which requires lifting the model to a higher-dimensional space.
 When projected to the original space, the continuous relaxation of the model is tighter than its Big-M equivalent \cite{grossmann_trespalacios_2013}.
@@
 \begin{equation}
-    \label{eq:ex_hull1}
+    \label{eq:ex_hull0}
     Ax_1 \leq by_1
@@
 \begin{equation}
-    \label{eq:ex_hull0}
+    \label{eq:ex_hull1}
     Cx_2 \leq dy_2
@@
 \begin{equation}
+    \label{eq:ex_hull4}
+    y_1 + y_2 = 1
+\end{equation}
+\begin{equation}
+    \label{eq:ex_hull5}
+    0 \leq x \leq U
+\end{equation}
+\begin{equation}
     \label{eq:ex_hull3}
     0 \leq x_i \leq U y_i \quad \forall i \in \{1,2\}
+\end{equation}
+\begin{equation}
+    \label{eq:ex_hull6}
+    y_1, y_2 \in \{0,1\}
 \end{equation}
@@
 
-Once the logic propositions are converted to CNF, each clause can be converted into an algebraic constraint with the following equivalence (Note: any negated Boolean variables, $\neg Y_i$, are replaced with $1-y_i$ in the reformulation),
+Once the logic propositions are converted to CNF, each clause can be converted into an algebraic constraint with the following equivalence, where the set $I$ represents the subset boolean variables present in the clause, and the set $J$ represents the subset of boolean variables present in the clause in negated form,
 
 \begin{align*}
-    \bigvee_{i \in I} Y_i & \ \ \text{becomes} \ \ \sum_{i\in I} y_i \geq 1 \\
+    \bigvee_{i \in I} Y_i \bigvee_{j \in J} (\neg Y_j) & \ \ \text{becomes} \ \ \sum_{i \in I} y_i + \sum_{j \in J} (1-y_j) \geq 1 \\
 \end{align*}
@@
 \begin{lstlisting}[language = Julia]
-using DisjunctiveProgramming, JuMP, HiGHS
+using DisjunctiveProgramming, HiGHS
 
 # create model
-m = JuMP.Model(HiGHS.Optimizer)
+m = GDPModel(HiGHS.Optimizer)
 # add variables to model
@@
 @variable(m, CRmin <= CR <= CRmax)
+# add logical variables to model
+@variable(m, YR[1:2], LogicalVariable)
+@variable(m, YS[1:2], LogicalVariable)
 
-# add constraints to model
+# add global constraints to model
 @constraints(m,
@@
 \begin{lstlisting}[language = Julia]
-@disjunction(m,
-    begin
-        F[5] == β[:S1]*F[4]
-        CS == γ[:S1]
-    end,
-    begin
-        F[5] == β[:S2]*F[4]
-        CS == γ[:S2]
-    end,
-    reformulation = :big_m, # reformulation type
-    name = :YS # symbol for indicator variable
-)
+# define constraints in left YS disjunct
+@constraint(m, F[5] == β[:S1]*F[4], DisjunctConstraint(YS[1]))
+@constraint(m, CS == γ[:S1], DisjunctConstraint(YS[1]))
+# define constraints in right YS disjunct
+@constraint(m, F[5] == β[:S2]*F[4], DisjunctConstraint(YS[2]))
+@constraint(m, CS == γ[:S2], DisjunctConstraint(YS[2]))
+# define disjunction (specify parent disjunct)
+@disjunction(m, YS, DisjunctConstraint(YR[2]))
 \end{lstlisting}
-    \item Define constraints in the outer disjunctions.
+    \item Define the outer disjunctions.
 \begin{lstlisting}[language = Julia]
-# define constraints in left disjunct
-R1_con = @constraints(m,
-    begin
-        F[6] == β[:R1]*F[2]
-        [i = 3:5], F[i] == 0
-        CR == γ[:R1]
-        CS == 0
-    end
-)
-
-# define constraints in right disjunct
-R2_con = @constraints(m,
-    begin
-        F[6] == β[:R2]*F[3]
-        CR == γ[:R2]      
-    end
-)
-\end{lstlisting}
-    \item Build the main disjunction using the constraint blocks defined in (3) and the \verb|add_disjunction!| function.
-Note that the reformulated constraints for the nested disjunction are stored in the \verb|.ext| dictionary of the model under the name of the disjunction (\verb|:YS| in this case).
-\begin{lstlisting}[language = Julia]
-add_disjunction!(m,
-    R1_con,
-    (
-        R2_con, #general constraints in R2 disj.
-        m.ext[:YS] #reformulated inner disj.
-    ),
-    reformulation = :big_m, # reformulation type
-    name = :YR # symbol for indicator variable
-)
+# define constraints in left YR disjunct
+@constraint(m, F[6] == β[:R1]*F[2], DisjunctConstraint(YR[1]))
+@constraint(m, [i = 3:5], F[i] == 0, DisjunctConstraint(YR[1]))
+@constraint(m, CR == γ[:R1], DisjunctConstraint(YR[1]))
+@constraint(m, CS == 0, DisjunctConstraint(YR[1]))
+# define constraints in right YR disjunct
+@constraint(m, F[6] == β[:R2]*F[3], DisjunctConstraint(YR[2]))
+@constraint(m, CR == γ[:R2], DisjunctConstraint(YR[2]))  
+# define disjunction
+@disjunction(m, YR)    
 \end{lstlisting}
@@
 \begin{lstlisting}[language = Julia]
-choose!(1, YR[1], YR[2]; mode = :exactly)
-choose!(YR[2], YS[1], YS[2]; mode = :exactly)
+@constraint(m, YR in Exactly(1))
+@constraint(m, YS in Exactly(YR[2]))
 \end{lstlisting}

### 2023-10-14 paper/paper.tex
update paper

@@
 \begin{align*}
-    \bigvee_{i \in I} Y_i \bigvee_{j \in J} (\neg Y_j) & \ \ \text{becomes} \ \ \sum_{i \in I} y_i + \sum_{j \in J} (1-y_j) \geq 1 \\
+    \left(\bigvee_{i \in I} Y_i\right) \vee \left(\bigvee_{j \in J} \neg Y_j\right) & \ \ \text{becomes} \ \ \sum_{i \in I} y_i + \sum_{j \in J} (1-y_j) \geq 1 \\
 \end{align*}
@@
 
-\subsection{Solution Techniques}
+\subsection{Other Solution Techniques} \label{other_techniques}
 
@@
 \subsection{Example}
-To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.3.3), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}.
+To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.4.0), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}.
 In this problem a chemical plant with two candidate reactor technologies ($R_1$ and $R_2$) must be designed.
@@
 # define constraints in left YS disjunct
-@constraint(m, F[5] == β[:S1]*F[4], DisjunctConstraint(YS[1]))
-@constraint(m, CS == γ[:S1], DisjunctConstraint(YS[1]))
+YS1_disjunct = DisjunctConstraint(YS[1])
+@constraint(m, F[5] == β[:S1]*F[4], YS1_disjunct)
+@constraint(m, CS == γ[:S1], YS1_disjunct)
 # define constraints in right YS disjunct
-@constraint(m, F[5] == β[:S2]*F[4], DisjunctConstraint(YS[2]))
-@constraint(m, CS == γ[:S2], DisjunctConstraint(YS[2]))
+YS2_disjunct = DisjunctConstraint(YS[2])
+@constraint(m, F[5] == β[:S2]*F[4], YS2_disjunct)
+@constraint(m, CS == γ[:S2], YS2_disjunct)
 # define disjunction (specify parent disjunct)
-@disjunction(m, YS, DisjunctConstraint(YR[2]))
+@disjunction(m, YS, YS2_disjunct)
 \end{lstlisting}
@@
 # define constraints in left YR disjunct
-@constraint(m, F[6] == β[:R1]*F[2], DisjunctConstraint(YR[1]))
-@constraint(m, [i = 3:5], F[i] == 0, DisjunctConstraint(YR[1]))
-@constraint(m, CR == γ[:R1], DisjunctConstraint(YR[1]))
-@constraint(m, CS == 0, DisjunctConstraint(YR[1]))
+YR1_disjunct = DisjunctConstraint(YR[1])
+@constraint(m, F[6] == β[:R1]*F[2], YR1_disjunct)
+@constraint(m, [i = 3:5], F[i] == 0, YR1_disjunct)
+@constraint(m, CR == γ[:R1], YR1_disjunct)
+@constraint(m, CS == 0, YR1_disjunct)
 # define constraints in right YR disjunct
-@constraint(m, F[6] == β[:R2]*F[3], DisjunctConstraint(YR[2]))
-@constraint(m, CR == γ[:R2], DisjunctConstraint(YR[2]))  
+YR2_disjunct = DisjunctConstraint(YR[2])
+@constraint(m, F[6] == β[:R2]*F[3], YR2_disjunct)
+@constraint(m, CR == γ[:R2], YR2_disjunct)  
 # define disjunction
@@
 \section{Future Work}
-The next steps for the \verb|DisjunctivePrograming.jl| package rely on extending \verb|JuMP.jl| further to allow creating GDP models that are not necessarily reformulated at model creation.
-Such models will allow using the different GDP solution strategies, such as direct reformulation to MI(N)LP, disjunctive branch and bound, logic-based outer approximation, hybrid cutting planes, and basic steps.
-The updated package will leverage existing JuMP extension infrastructure and make it possible to define indexing notation for disjunctions, a new Boolean variable type, and a new disjunciton constraint type.
-These improvements are expected to make the package more usable, flexible, and performant for advanced applications of GDP in JuMP.
+Since the package is currently limited to reformulating GDP models into Mixed-Integer Programming JuMP models, future work includes developing logic-based solvers to allow optimizing GDP models directly.
+This will include GDP solvers that implement the other solution techniques described in Section \ref{other_techniques}.
+Future work also involves extending the list of suported reformulation techniques to include the \textit{P-Split} \cite{kronqvist2022p} and \textit{True-False} \cite{agarwal2015novel} reformulations.
 

### 2023-10-14 docs/make.jl
add readme to docs

@@ -4,7 +4,8 @@ makedocs(
     sitename = "DisjunctiveProgramming.jl",
     modules  = [DisjunctiveProgramming],
     pages=[
-        "Home" => "index.md"
+        "Home" => "index.md",
+        "API" => "api.md"
     ],
     checkdocs = :none
 )

### 2023-10-14 paper/paper.tex
update refs

@@
 Within the optimization community, there is a high volume of ongoing research that relies on GDP to formulate models for a variety of applications.
-Due to the combinatorial nature of system design problems, the GDP paradigm has been applied to the synthesis of complex processes and networks \cite{MATOVU2022107856, ZHOU202269}, the planning and optimal control of energy systems \cite{CHO2022841, kim2022generalized}, and the modeling of chemical synthesis under uncertainty \cite{CHEN2022107616}.
+Due to the combinatorial nature of system design problems, the GDP paradigm has been applied to the synthesis of complex processes and networks \cite{MATOVU2022107856, ZHOU202269}, the planning and optimal control of energy systems \cite{CHO2022841}, and the modeling of chemical synthesis under uncertainty \cite{CHEN2022107616}.
 These and numerous other applications of GDP illustrate the benefit of having a robust package for GDP that removes much of the overhead associated with developing and testing GDP models.

### 2023-10-14 paper/paper.tex

@@
 \subsection{Example}
-To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.4.0), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}.
+To illustrate the syntax in \verb|DisjunctiveProgramming.jl| (Version 0.4.1), consider the simple superstructure optimization problem for the chemical process given in Figure \ref{fig:superstruct_opt_diagram}.
 In this problem a chemical plant with two candidate reactor technologies ($R_1$ and $R_2$) must be designed.

### 2023-10-14 dev/search_index.js
build based on 4b522a3

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"#Overview","page":"Home","title":"Overview","text":"","category":"section"},{"location":"","page":"Home","title":"Home","text":"DisjunctiveProgramming.jl","category":"page"}]
+[{"location":"api/#API","page":"API","title":"API","text":"","category":"section"},{"location":"api/","page":"API","title":"API","text":"Modules = [DisjunctiveProgramming]\nOrder   = [:type, :function]","category":"page"},{"location":"api/#DisjunctiveProgramming.AbstractReformulationMethod","page":"API","title":"DisjunctiveProgramming.AbstractReformulationMethod","text":"AbstractReformulationMethod <: AbstractSolutionMethod\n\nAn abstract type for reformulation approaches used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AbstractSolutionMethod","page":"API","title":"DisjunctiveProgramming.AbstractSolutionMethod","text":"AbstractSolutionMethod\n\nAn abstract type for solution methods used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtLeast","page":"API","title":"DisjunctiveProgramming.AtLeast","text":"AtLeast{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtLeast.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtMost","page":"API","title":"DisjunctiveProgramming.AtMost","text":"AtMost{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtMost.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.BigM","page":"API","title":"DisjunctiveProgramming.BigM","text":"BigM <: AbstractReformulationMethod\n\nA type for using the big-M reformulation approach for disjunctive constraints.\n\nFields\n\nvalue::Float64: Big-M value (default = 1e9).\ntight::Bool: Attempt to tighten the Big-M value (default = true)?\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.ConstraintData","page":"API","title":"DisjunctiveProgramming.ConstraintData","text":"ConstraintD
[…]

### 2023-10-14 v0.4.1/search_index.js
build based on 3af4402

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"api/#API","page":"API","title":"API","text":"","category":"section"},{"location":"api/","page":"API","title":"API","text":"Modules = [DisjunctiveProgramming]\nOrder   = [:type, :function]","category":"page"},{"location":"api/#DisjunctiveProgramming.AbstractReformulationMethod","page":"API","title":"DisjunctiveProgramming.AbstractReformulationMethod","text":"AbstractReformulationMethod <: AbstractSolutionMethod\n\nAn abstract type for reformulation approaches used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AbstractSolutionMethod","page":"API","title":"DisjunctiveProgramming.AbstractSolutionMethod","text":"AbstractSolutionMethod\n\nAn abstract type for solution methods used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtLeast","page":"API","title":"DisjunctiveProgramming.AtLeast","text":"AtLeast{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtLeast.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtMost","page":"API","title":"DisjunctiveProgramming.AtMost","text":"AtMost{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtMost.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.BigM","page":"API","title":"DisjunctiveProgramming.BigM","text":"BigM <: AbstractReformulationMethod\n\nA type for using the big-M reformulation approach for disjunctive constraints.\n\nFields\n\nvalue::Float64: Big-M value (default = 1e9).\ntight::Bool: Attempt to tighten the Big-M value (default = true)?\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.ConstraintData","page":"API","title":"DisjunctiveProgramming.ConstraintData","text":"ConstraintData{C <: JuMP.AbstractConstraint}\n\nA type for storing constraint objects in GDPData and any meta-data  they possess.\n\nFields\n\nconstraint::C: The constraint.\nname::String: The na
[…]

### 2023-10-14 versions.js

@@ -1,9 +1,10 @@
 var DOC_VERSIONS = [
   "stable",
+  "v0.4",
   "v0.3",
   "v0.2",
   "v0.1",
   "dev",
 ];
-var DOCUMENTER_NEWEST = "v0.3.6";
+var DOCUMENTER_NEWEST = "v0.4.1";
 var DOCUMENTER_STABLE = "stable";

### 2023-10-14 src/logic.jl
remove unused function

@@ -29,22 +29,6 @@ for (name, alt, head, func) in (
     end
 end
 
-"""
-    to_cnf!(expr::Expr)
-
-Convert an expression of symbolic Boolean variables and operators to CNF.
-"""
-function to_cnf!(expr::Expr)
-    check_logical_proposition(expr) #check that valid boolean symbols and variables are used in the logical proposition
-    eliminate_equivalence!(expr) #eliminate ⇔
-    eliminate_implication!(expr) #eliminmate ⇒
-    move_negations_inwards!(expr) #expand ¬
-    clause_list = distribute_and_over_or_recursively!(expr) #distribute ∧ over ∨ recursively
-    @assert !isempty(clause_list) "Conversion to CNF failed."
-
-    return clause_list
-end
-
 ################################################################################
 #                            CONJUNCTIVE NORMAL FORM
 ################################################################################

### 2023-10-14 dev/search_index.js
build based on afed95f

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"api/#API","page":"API","title":"API","text":"","category":"section"},{"location":"api/","page":"API","title":"API","text":"Modules = [DisjunctiveProgramming]\nOrder   = [:type, :function]","category":"page"},{"location":"api/#DisjunctiveProgramming.AbstractReformulationMethod","page":"API","title":"DisjunctiveProgramming.AbstractReformulationMethod","text":"AbstractReformulationMethod <: AbstractSolutionMethod\n\nAn abstract type for reformulation approaches used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AbstractSolutionMethod","page":"API","title":"DisjunctiveProgramming.AbstractSolutionMethod","text":"AbstractSolutionMethod\n\nAn abstract type for solution methods used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtLeast","page":"API","title":"DisjunctiveProgramming.AtLeast","text":"AtLeast{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtLeast.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtMost","page":"API","title":"DisjunctiveProgramming.AtMost","text":"AtMost{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtMost.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.BigM","page":"API","title":"DisjunctiveProgramming.BigM","text":"BigM <: AbstractReformulationMethod\n\nA type for using the big-M reformulation approach for disjunctive constraints.\n\nFields\n\nvalue::Float64: Big-M value (default = 1e9).\ntight::Bool: Attempt to tighten the Big-M value (default = true)?\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.ConstraintData","page":"API","title":"DisjunctiveProgramming.ConstraintData","text":"ConstraintData{C <: JuMP.AbstractConstraint}\n\nA type for storing constraint objects in GDPData and any meta-data  they possess.\n\nFields\n\nconstraint::C: The constraint.\nname::String: The na
[…]

### 2023-10-14 src/model.jl
remove unused function

@@ -49,16 +49,6 @@ function is_gdp_model(model::JuMP.Model)
     return haskey(model.ext, :GDP)
 end
 
-"""
-    disjunction_indicators(disjunction::DisjunctionRef) 
-
-Return LogicalVariableRefs associated with a disjunction.
-"""
-function disjunction_indicators(disjunction::DisjunctionRef) 
-    model, idx = disjunction.model, disjunction.index
-    return _disjunctions(model)[idx].constraint.indicators
-end
-
 # Create accessors for GDP data fields
 _logical_variables(model::JuMP.Model) = gdp_data(model).logical_variables
 _logical_constraints(model::JuMP.Model) = gdp_data(model).logical_constraints

### 2023-10-14 src/reformulate.jl
remove unused functions

@@ -122,9 +122,6 @@ function _reformulate_disjunct(model::JuMP.Model, ref_cons::Vector{JuMP.Abstract
     return
 end
 
-_index_to_constraint(model::JuMP.Model, cidx::DisjunctConstraintIndex) = _disjunct_constraints(model)[cidx]
-_index_to_constraint(model::JuMP.Model, cidx::DisjunctionIndex) = _disjunctions(model)[cidx]
-
 # reformulation for nested disjunction
 # NOTE: name of inner disjunction (if given) is currently lost (not passed upwards)
 function reformulate_disjunct_constraint(

### 2023-10-14 dev/search_index.js
build based on 37cc24d

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"api/#API","page":"API","title":"API","text":"","category":"section"},{"location":"api/","page":"API","title":"API","text":"Modules = [DisjunctiveProgramming]\nOrder   = [:type, :function]","category":"page"},{"location":"api/#DisjunctiveProgramming.AbstractReformulationMethod","page":"API","title":"DisjunctiveProgramming.AbstractReformulationMethod","text":"AbstractReformulationMethod <: AbstractSolutionMethod\n\nAn abstract type for reformulation approaches used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AbstractSolutionMethod","page":"API","title":"DisjunctiveProgramming.AbstractSolutionMethod","text":"AbstractSolutionMethod\n\nAn abstract type for solution methods used to solve GDPModels.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtLeast","page":"API","title":"DisjunctiveProgramming.AtLeast","text":"AtLeast{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtLeast.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.AtMost","page":"API","title":"DisjunctiveProgramming.AtMost","text":"AtMost{T<:Union{Int,LogicalVariableRef}} <: JuMP.AbstractVectorSet\n\nConvenient alias for using _MOIAtMost.\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.BigM","page":"API","title":"DisjunctiveProgramming.BigM","text":"BigM <: AbstractReformulationMethod\n\nA type for using the big-M reformulation approach for disjunctive constraints.\n\nFields\n\nvalue::Float64: Big-M value (default = 1e9).\ntight::Bool: Attempt to tighten the Big-M value (default = true)?\n\n\n\n\n\n","category":"type"},{"location":"api/#DisjunctiveProgramming.ConstraintData","page":"API","title":"DisjunctiveProgramming.ConstraintData","text":"ConstraintData{C <: JuMP.AbstractConstraint}\n\nA type for storing constraint objects in GDPData and any meta-data  they possess.\n\nFields\n\nconstraint::C: The constraint.\nname::String: The nam
[…]

### 2023-10-14 src/variables.jl
bug fix

@@ -23,14 +23,14 @@ function JuMP.build_variable(
         _error("Logical variables cannot have bounds.")
     elseif info.integer
         _error("Logical variables cannot be integer valued.")
-    elseif info.has_fix && !isone(info.fix) && !iszero(info.fix)
-        _error("Invalid fix value, must be 0 or 1.")
+    elseif info.has_fix && !isone(info.fixed_value) && !iszero(info.fixed_value)
+        _error("Invalid fix value, must be false or true.")
     elseif info.has_start && !isone(info.start) && !iszero(info.start)
-        _error("Invalid start value, must be 0 or 1.")
+        _error("Invalid start value, must be false or true.")
     end
 
     # create the variable
-    fix = info.has_fix ? Bool(info.fix) : nothing
+    fix = info.has_fix ? Bool(info.fixed_value) : nothing
     start = info.has_start ? Bool(info.start) : nothing
     return LogicalVariable(fix, start)
 end

### 2023-10-14 src/constraints.jl
add tests

@@ -379,7 +379,7 @@ function disjunction(
     model::JuMP.Model, 
     disjunct_indicators, 
     nested_tag::DisjunctConstraint,
-    name::String = "",
+    name::String = ""
 ) # TODO add kw argument to build exactly 1 constraint
     return _disjunction(error, model, disjunct_indicators, name, nested_tag)
 end

### 2023-10-14 test/constraints/disjunct.jl

@@ -7,6 +7,7 @@ function test_disjunct_add_fail()
     @variable(model, w, Logical)
     @variable(model, z, Bin)
     @test_macro_throws UndefVarError @constraint(model, z == 1, DisjunctConstraint(w)) # binary variable
+    @test_throws ErrorException build_constraint(error, 1z, MOI.EqualTo(1), DisjunctConstraint(w)) # binary variable
 end
 
 function test_disjunct_add_success()

### 2023-10-14 test/disjunction.jl

@@ -3,14 +3,17 @@ function test_disjunction_add_fail()
     @variable(model, x)
     @variable(model, y[1:2], Logical)
     @constraint(model, x == 5, DisjunctConstraint(y[1]))
-
+    
     @test_macro_throws ErrorException @disjunction(model) #not enough arguments
     @test_macro_throws UndefVarError @disjunction(model, y) #unassociated indicator
     @test_macro_throws UndefVarError @disjunction(GDPModel(), y) #wrong model
     @test_macro_throws ErrorException @disjunction(Model(), y) #not a GDPModel
     @test_macro_throws UndefVarError @disjunction(model, [y[1], y[1]]) #duplicate indicator
-    @test_macro_throws UndefVarError @disjunction(model, y[1]) #no disjunction expression
+    @test_macro_throws UndefVarError @disjunction(model, y[1]) #unrecognized disjunction expression
+    @test_throws ErrorException disjunction(model, y[1]) #unrecognized disjunction expression
+    @test_throws ErrorException disjunction(model, [1]) #unrecognized disjunction expression
     @test_macro_throws UndefVarError @disjunction(model, y, "random_arg") #unrecognized extra argument
+    @test_throws ErrorException DP._disjunction(error, model, y, "y", "random_arg") #unrecognized extra argument
     @test_macro_throws ErrorException @disjunction(model, "ABC") #unrecognized structure
     @test_macro_throws ErrorException @disjunction(model, begin y end) #@disjunctions (plural)
     @test_macro_throws UndefVarError @disjunction(model, x, y) #name x already exists
@@ -104,6 +107,16 @@ function test_disjunction_add_sparse_axis()
     @test length(disj) == 3
     @test disj.names == (:i, :j)
     @test Set(keys(disj.data)) == Set([(1,2),(1,3),(2,3)])
+end
+
+function test_disjunctions_add_fail()
+    model = GDPModel()
+    @variable(model, x)
+    @variable(model, y[1:2], Logical)
+    @variable(model, z[1:2], Logical)
+    @constraint(model, x <= 5, DisjunctConstraint(y[1]))
+    @constraint(model, x >= 5, DisjunctConstraint(y[2]))
+    @test_macro_throws ErrorException @disjunctions(model, y)
 end
 
 function test_disjunctions_add_success()
@@ -203,6 +216,7 @@ end
         test_disjunction_add_array()
         test_disjunciton_add_dense_axis()
         test_disjunction_add_sparse_axis()
[…]

### 2023-10-14 test/runtests.jl

@@ -27,6 +27,7 @@ end
 
 include("aqua.jl")
 include("model.jl")
+include("jump.jl")
 include("variables/query.jl")
 include("variables/logical.jl")
 include("constraints/selector.jl")
@@ -35,5 +36,6 @@ include("constraints/disjunct.jl")
 include("constraints/indicator.jl")
 include("constraints/bigm.jl")
 include("constraints/hull.jl")
+include("constraints/fallback.jl")
 include("disjunction.jl")
 include("solve.jl")

### 2023-10-14 test/variables/logical.jl

@@ -1,7 +1,21 @@
 # test creating, modifying, and reformulating logical variables
+
+function test_base()
+    model = GDPModel()
+    @variable(model, y, Logical)
+    @test Base.broadcastable(y) isa Base.RefValue{LogicalVariableRef}
+    @test length(y) == 1
+end
+
 function test_lvar_add_fail()
    model = Model()
    @test_throws ErrorException @variable(model, y, Logical)
+   @test_throws ErrorException @variable(model, y, Logical; kwarg=true)
+   @test_throws ErrorException @variable(model, 0 <= y, Logical)
+   @test_throws ErrorException @variable(model, y <= 1, Logical)
+   @test_throws ErrorException @variable(model, y, Logical, integer=true)
+   @test_throws ErrorException @variable(model, y, Logical, start=2)
+   @test_throws ErrorException @variable(model, y == 2, Logical)
 end
 
 function test_lvar_add_success()
@@ -75,6 +89,12 @@ function test_lvar_set_start_value()
     test_lvar_reformulation(model, y)
 end
 
+function test_lvar_creation_fix_value()
+    model = GDPModel()
+    @variable(model, y == true, Logical)
+    @test fix_value(y)
+end
+
 function test_lvar_fix_value()
     model = GDPModel()
     @variable(model, y, Logical)
@@ -146,6 +166,9 @@ function test_lvar_reformulation(model::Model, lvref::LogicalVariableRef)
 end
 
 @testset "Logical Variables" begin
+    @testset "Base Methods" begin
+        test_base()
+    end
     @testset "Add Logical Variables" begin
         test_lvar_add_fail()
         test_lvar_add_success()
@@ -157,6 +180,7 @@ end
         test_lvar_set_name()
         test_lvar_creation_start_value()
         test_lvar_set_start_value()
+        test_lvar_creation_fix_value()
         test_lvar_fix_value()
     end
     @testset "Delete Logical Variables" begin

### 2023-10-16 src/bigm.jl
remove JuMP prefix

@@ -2,7 +2,7 @@
 #                              BIG-M VALUE
 ################################################################################
 # Get Big-M value for a particular constraint
-function _get_M_value(func::JuMP.AbstractJuMPScalar, set::_MOI.AbstractSet, method::BigM)
+function _get_M_value(func::AbstractJuMPScalar, set::_MOI.AbstractSet, method::BigM)
     if method.tighten
         M = _get_tight_M(func, set, method)
     else
@@ -12,7 +12,7 @@ function _get_M_value(func::JuMP.AbstractJuMPScalar, set::_MOI.AbstractSet, meth
 end
 
 # Get the tightest Big-M value for a particular constraint
-function _get_tight_M(func::JuMP.AbstractJuMPScalar, set::_MOI.AbstractSet, method::BigM)
+function _get_tight_M(func::AbstractJuMPScalar, set::_MOI.AbstractSet, method::BigM)
     M = min.(method.value, _calculate_tight_M(func, set, method)) #broadcast for when S <: MOI.Interval or MOI.EqualTo or MOI.Zeros
     if any(isinf.(M))
         error("A finite Big-M value must be used. The value obtained was $M.")
@@ -21,14 +21,14 @@ function _get_tight_M(func::JuMP.AbstractJuMPScalar, set::_MOI.AbstractSet, meth
 end
 
 # Get user-specified Big-M value
-function _get_M(::JuMP.AbstractJuMPScalar, ::Union{_MOI.LessThan, _MOI.GreaterThan, _MOI.Nonnegatives, _MOI.Nonpositives}, method::BigM)
+function _get_M(::AbstractJuMPScalar, ::Union{_MOI.LessThan, _MOI.GreaterThan, _MOI.Nonnegatives, _MOI.Nonpositives}, method::BigM)
     M = method.value
     if isinf(M)
         error("A finite Big-M value must be used. The value given was $M.")
     end
     return M
 end
-function _get_M(::JuMP.AbstractJuMPScalar, ::Union{_MOI.Interval, _MOI.EqualTo, _MOI.Zeros}, method::BigM)
+function _get_M(::AbstractJuMPScalar, ::Union{_MOI.Interval, _MOI.EqualTo, _MOI.Zeros}, method::BigM)
     M = method.value
     if isinf(M)
         error("A finite Big-M value must be used. The value given was $M.")
[…]

### 2023-10-16 src/constraints.jl

@@ -45,17 +45,17 @@ for (RefType, loc) in ((:DisjunctConstraintRef, :disjunct_constraints),
         JuMP.index(cref::$RefType) = cref.index
 
         @doc """
-            JuMP.is_valid(model::JuMP.Model, cref::$($RefType))
+            JuMP.is_valid(model::Model, cref::$($RefType))
 
         Return `true` if `cref` refers to a valid constraint in the `GDP model`.
         """
-        function JuMP.is_valid(model::JuMP.Model, cref::$RefType) # TODO: generalize for AbstractModel
-            return model === JuMP.owner_model(cref)
+        function JuMP.is_valid(model::Model, cref::$RefType) # TODO: generalize for AbstractModel
+            return model === owner_model(cref)
         end
 
         # Get the ConstraintData object
         function _constraint_data(cref::$RefType)
-            return gdp_data(JuMP.owner_model(cref)).$loc[JuMP.index(cref)]
+            return gdp_data(owner_model(cref)).$loc[index(cref)]
         end
 
         @doc """
@@ -74,7 +74,7 @@ for (RefType, loc) in ((:DisjunctConstraintRef, :disjunct_constraints),
         """
         function JuMP.set_name(cref::$RefType, name::String)
             _constraint_data(cref).name = name
-            _set_ready_to_optimize(JuMP.owner_model(cref), false)
+            _set_ready_to_optimize(owner_model(cref), false)
             return
         end
 
@@ -94,25 +94,25 @@ for (RefType, loc) in ((:DisjunctConstraintRef, :disjunct_constraints),
         end
         Base.copy(cref::$RefType) = cref
         @doc """
-            Base.getindex(map::JuMP.GenericReferenceMap, cref::$($RefType))
+            Base.getindex(map::GenericReferenceMap, cref::$($RefType))
 
         ...
         """
-        function Base.getindex(map::JuMP.ReferenceMap, cref::$RefType)
-            $RefType(map.model, JuMP.index(cref))
+        function Base.getindex(map::ReferenceMap, cref::$RefType)
+            $RefType(map.model, index(cref))
         end
     end
 end
 
 # Extend delete
 """
-    JuMP.delete(model::JuMP.Model, cref::DisjunctionRef)
+    JuMP.delete(model::Model, cref::DisjunctionRef)
 
 Delete a disjunction constraint from the `GDP model`.
 """
[…]

### 2023-10-16 src/indicator.jl

@@ -3,32 +3,32 @@
 ################################################################################
 #scalar disjunct constraint
 function reformulate_disjunct_constraint(
-    model::JuMP.Model,
-    con::JuMP.ScalarConstraint{T, S},
-    bvref::JuMP.VariableRef,
+    model::Model,
+    con::ScalarConstraint{T, S},
+    bvref::VariableRef,
     method::Indicator
 ) where {T, S}
-    reform_con = JuMP.build_constraint(error, [1*bvref, con.func], _MOI.Indicator{_MOI.ACTIVATE_ON_ONE}(con.set))
+    reform_con = build_constraint(error, [1*bvref, con.func], _MOI.Indicator{_MOI.ACTIVATE_ON_ONE}(con.set))
     return [reform_con]
 end
 #vectorized disjunct constraint
 function reformulate_disjunct_constraint(
-    model::JuMP.Model,
-    con::JuMP.VectorConstraint{T, S},
-    bvref::JuMP.VariableRef,
+    model::Model,
+    con::VectorConstraint{T, S},
+    bvref::VariableRef,
     method::Indicator
 ) where {T, S}
     set = _vec_to_scalar_set(con.set)
     return [
-        JuMP.build_constraint(error, [1*bvref, f], _MOI.Indicator{_MOI.ACTIVATE_ON_ONE}(set)) 
+        build_constraint(error, [1*bvref, f], _MOI.Indicator{_MOI.ACTIVATE_ON_ONE}(set)) 
         for f in con.func
     ]
 end
 #nested indicator reformulation. NOTE: the user needs to provide the appropriate linking constraint for the logical variables for this to work (e.g. w in Exactly(y[1]) to link the parent disjunct y[1] to the nested disjunction w)
 function reformulate_disjunct_constraint(
-    model::JuMP.Model,
-    con::JuMP.VectorConstraint{T, S},
-    bvref::JuMP.VariableRef,
+    model::Model,
+    con::VectorConstraint{T, S},
+    bvref::VariableRef,
     method::Indicator
 ) where {T, S <: _MOI.Indicator}
     return [con]

### 2023-10-16 src/macros.jl

@@ -111,7 +111,7 @@ function _error_if_cannot_register(
     model, 
     name::Symbol
     )
-    if haskey(JuMP.object_dictionary(model), name)
+    if haskey(object_dictionary(model), name)
         _error("An object of name $name is already attached to this model. If ",
                "this is intended, consider using the anonymous construction ",
                "syntax, e.g., `x = @macro_name(model, ...)` where the name ",
@@ -248,7 +248,7 @@ macro disjunction(model, args...)
         _add_kwargs(creation_code, extra_kwargs)
     else
         # we have a container of parameters
-        idxvars, inds = JuMP.Containers.build_ref_sets(_error, c)
+        idxvars, inds = Containers.build_ref_sets(_error, c)
         if model in idxvars
             _error("Index $(model) is the same symbol as the model. Use a ",
                    "different name for the index.")
@@ -257,7 +257,7 @@ macro disjunction(model, args...)
         disjunction_call = :( _disjunction($_error, $esc_model, $x, $name_code) )
         _add_positional_args(disjunction_call, extra)
         _add_kwargs(disjunction_call, extra_kwargs)
-        creation_code = JuMP.Containers.container_code(idxvars, inds, disjunction_call,
+        creation_code = Containers.container_code(idxvars, inds, disjunction_call,
                                                        container_type)
     end
 

### 2023-12-11 paper/paper.tex
update equations to align* blocks

@@
 When nonlinearities arrise in either the feasible space or the objective function, they are called mixed-integer nonlinear programs (MINLP).
-\vskip 6pt
+
 A more systematic approach to modeling such systems is to use Generalized Disjunctive Programming (GDP) \cite{chen_grossmann_2019, grossmann_trespalacios_2013}, which generalizes the Disjunctive Programming paradigm proposed by Balas \cite{balas_2018}.
@@
 It is also often possible to exploit the explicit logical structure of a GDP model to provide tighter relaxations than corresponding MIP models, which may improve convergence speed and robustness for solutions via advanced solution algorithms \cite{chen_grossmann_2019}.
-\vskip 6pt
+
 Within the optimization community, there is a high volume of ongoing research that relies on GDP to formulate models for a variety of applications.
@@
 Although packages with GDP capabilities exist for \verb|Pyomo| \cite{chen2022pyomo} and \verb|GAMS| \cite{vecchietti1999logmip}, having such a package available in Julia can greatly accelerate research in optimization, where packages like \verb|JuMP.jl| \cite{dunning_huchette_lubin_2017} are gaining significant traction.
-\vskip 6pt
+
 This paper provides background on the GDP paradigm, and the techniques for reformulating and solving such models.
@@
 The two main reformulation strategies to transform GDP models into their equivalent MIP models are the Big-M reformulation \cite{nemhauser_1999, TRESPALACIOS201598} and the Hull reformulation \cite{LEE20002125}, the latter of which yields tighter models at the expense of larger model sizes \cite{grossmann_lee_2003}.
-\vskip 6pt
 
@@
 
-The general notation for a GDP problem is given in Eq. \eqref{eq:general_gdp} - \eqref{eq:general_gdp1}.
-\begin{align}
-    \label{eq:general_gdp}
+The general notation for a GDP problem is given below,
+\begin{align*}
     \min \ &f(x) \\
@@
     & Y_{ik} \in \{true, false\} \quad \forall i \in J_k, k \in K\\
-    \label{eq:general_gdp1}
     & x \in X \subseteq \mathbb{R}^n
-\end{align}
+\end{align*}
 Here $f(x)$ is the objective function to be minimized over the continuous variable $x$, $g(x)$ represents the global constraints, $h(x)$ represents the disjunct-specific constraints, and $Y$ is the Boolean variable governing each disjunction.
@@
 These can take the form of logical propositions or constraint programming expressions.
-\vskip 6pt
 
-In the case of a linear objective function and constraint set, the GDP model can be written as Eq. \eqref{eq:lgdp} - \eqref{eq:lgdp2}.
-\begin{align}
-    \label{eq:lgdp}
+In the case of a linear objective function and constraint set, the GDP model can be written as,
+\begin{align*}
     \min \ & c^Tx \\
@@
     & \Omega(Y) = true \\
-    \label{eq:lgdp2}
     & Y_{ik} \in \{true, false\} \quad \forall i \in J_k, k \in K
-\end{align}
-\vskip 6pt
+\end{align*}
 
 \subsection{Solution Technique: Reformulation to Mixed-Integer Program}
-The simplest example of a linear GDP system is given in \eqref{eq:ex} - \eqref{eq:y}, where $Y_i$ is a Boolean indicator variable that enforces the constraints in the disjunct ($Ax \le b$ or $Cx \le d$) when $true$.
-\vskip 6pt
-\begin{equation}
-    \label{eq:ex}
-    \begin{bmatrix}
+The simplest example of a linear GDP system is given below, where $Y_i$ is a Boolean indicator variable that enforces the constraints in the disjunct ($Ax \le b$ or $Cx \le d$) when $true$,
+
+\begin{align*}
+    & \begin{bmatrix}
     Y_1 \\ Ax \leq b
@@
         Y_2 \\ Cx \leq d
-    \end{bmatrix}
-\end{equation}
-\begin{equation}
-    \label{eq:x}
-    0 \leq x \leq U
-\end{equation}
-\begin{equation}
-    \label{eq:simple_xor}
-    Y_1 \ \underline{\vee} \ Y_2
-\end{equation}
-\begin{equation}
-    \label{eq:y}
-    Y_1, Y_2 \in \{true, false\}
-\end{equation}
-\vskip 6pt
+    \end{bmatrix} \\
+    & 0 \leq x \leq U \\
+    & Y_1 \ \underline{\vee} \ Y_2 \\
+    & Y_1, Y_2 \in \{true, false\}
+\end{align*}
 
@@
 The rectangle on the right is defined by the constraints in the right disjunct, $Cx \le d$.
-The non-overlapping nature of the two regions is supported by the exclusive-OR relationship in Eq.
-\eqref{eq:simple_xor}.
+The non-overlapping nature of the two regions is supported by the exclusive-OR relationship above.
 
@@
 \end{figure}
-\vskip 6pt
 
  \subsubsection{Big-M Reformulation}
- The Big-M reformulation for this problem is given by \eqref{eq:ex_bigm1} - \eqref{eq:ex_bigm5}, where $M$ is a sufficiently large scalar that makes the particular constraint redundant when its indicator variable is not selected (i.e., $y_i = 0$).
+ The Big-M reformulation for this problem is given below, where $M$ is a sufficiently large scalar that makes the particular constraint redundant when its indicator variable is not selected (i.e., $y_i = 0$).
 Note that the Boolean variables, $Y_i$, are replaced by binary variables, $y_i$.
-When the integrality constraint in Eq.
-\eqref{eq:ex_bigm4} is relaxed to $0 \leq x_1, x_2 \leq 1$, the resulting feasible region can be visualized by projecting the relaxed model onto the $x_1, x_2$ plane.
+When the integrality constraint $y_1,y_2 \in \{0,1\}$ is relaxed to $0 \leq x_1, x_2 \leq 1$, the resulting feasible region can be visualized by projecting the relaxed model onto the $x_1, x_2$ plane.
 This results in the region encapsulated by the dashed line in Figure \ref{fig:bigm}.
@@
 
-\begin{equation}
-    \label{eq:ex_bigm1}
-    Ax \leq b + M \cdot (1 - y_1)
-\end{equation}
-\begin{equation}
-    \label{eq:ex_bigm2}
-    Cx \leq d + M \cdot (1 - y_2)
-\end{equation}
-\begin{equation}
-    \label{eq:ex_bigm3}
-    y_1 + y_2 = 1
-\end{equation}
-\begin{equation}
-    \label{eq:ex_bigm4}
-    0 \leq x \leq U
-\end{equation}
-\begin{equation}
-    \label{eq:ex_bigm5}
-    y_1, y_2 \in \{0,1\}
-\end{equation}
+\begin{align*}
+    & Ax \leq b + M \cdot (1 - y_1) \\
+    & Cx \leq d + M \cdot (1 - y_2) \\
+    & y_1 + y_2 = 1 \\
+    & 0 \leq x \leq U \\
+    & y_1, y_2 \in \{0,1\}
+\end{align*}
 
@@
 \subsubsection{Hull Reformulation}
-The Hull reformulation is given by \eqref{eq:ex_hull0} - \eqref{eq:ex_hull6}, which requires lifting the model to a higher-dimensional space.
+The Hull reformulation is given below.
+This formulation requires lifting the model to a higher-dimensional space.
 When projected to the original space, the continuous relaxation of the model is tighter than its Big-M equivalent \cite{grossmann_trespalacios_2013}.
@@
 
-\begin{equation}
-    \label{eq:ex_hull0}
-    Ax_1 \leq by_1
-\end{equation}
-\begin{equation}
-    \label{eq:ex_hull1}
-    Cx_2 \leq dy_2
-\end{equation}
-\begin{equation}
-    \label{eq:ex_hull2}
-    x = x_1 + x_2
-\end{equation}
-\begin{equation}
-    \label{eq:ex_hull4}
-    y_1 + y_2 = 1
-\end{equation}
-\begin{equation}
-    \label{eq:ex_hull5}
-    0 \leq x \leq U
-\end{equation}
-\begin{equation}
-    \label{eq:ex_hull3}
-    0 \leq x_i \leq U y_i \quad \forall i \in \{1,2\}
-\end{equation}
-\begin{equation}
-    \label{eq:ex_hull6}
-    y_1, y_2 \in \{0,1\}
-\end{equation}
+\begin{align*}
+    & Ax_1 \leq by_1 \\
+    & Cx_2 \leq dy_2 \\
+    & x = x_1 + x_2 \\ 
+    & y_1 + y_2 = 1 \\ 
+    & 0 \leq x \leq U \\
+    & 0 \leq x_i \leq U y_i \quad \forall i \in \{1,2\} \\
+    & y_1, y_2 \in \{0,1\}
+\end{align*}
 
-\begin{figure}%[H]
+\begin{figure}
     \centering
@@
 \end{figure}
-\vskip 6pt
 
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[scale=0.6]{superstructure_pfd.png}
+    \caption{Illustrative superstructure optimization problem}
+    \label{fig:superstruct_opt_diagram}
+\end{figure*}
+
 \section{DisjunctiveProgramming.jl}
@@
 
-\vskip 6pt
 Logical propositions can be added to JuMP models using expressions involving the disjunction indicator variables and the standard Boolean operators ($\Leftrightarrow, \Rightarrow, \vee, \wedge, \text{ and } \neg$) in an \verb|@proposition| macro.
@@
 
-\vskip 6pt
 Nesting of disjunctions is also supported.
@@
 If the second reactor technology is chosen, a separation system must also be installed, for which two separation technologies ($S_1$ and $S_2$) are available.
-The GDP model seeks to maximize the product flow ($F_7$), while discounting for reactor ($C_R$) and separator ($C_S$) installation costs as given in \eqref{eq:example_obj}, subject to the nested disjunction in \eqref{eq:example_gdp} and the global mass balances in \eqref{eq:example_global}
-- \eqref{eq:example_global1}.
-The system variables are the flows on each stream $i$ ($F_i$) and the installation costs, with their respective bounds given in \eqref{eq:example_var1} - \eqref{eq:example_var3}.
+The GDP model seeks to maximize the final product flow ($F_7$), while discounting for reactor and separator installation costs ($C_R$ and $C_S$, respectively), subject to the nested disjunction and the global mass balances on the stream flows $F_i$.
+The system variables are the flows on each stream $i$ ($F_i$) and the installation costs, with their respective bounds given in problem formulation.
 The fixed cost and process yield parameters are given by $\gamma$ and $\beta$, respectively.
 
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.4]{superstructure_pfd.png}
-    \caption{Illustrative superstructure optimization problem}
-    \label{fig:superstruct_opt_diagram}
-\end{figure}
-
-\begin{equation}
-    \label{eq:example_obj}
-    \max F_7 - C_R - C_S
-\end{equation}
-\begin{equation}
-    \label{eq:example_gdp}
-    \begin{bmatrix}
+\begin{align*}
+    \max \ &  F_7 - C_R - C_S \\
+    \text{s.t.} \ & \\
+    &\begin{bmatrix}
         Y_{R1} \\
@@
         \end{bmatrix}
-    \end{bmatrix}
-\end{equation}
-\begin{equation}
-    \label{eq:example_global}
-    F_1 = F_2 + F_3
-\end{equation}
-\begin{equation}
-    \label{eq:example_global1}
-    F_7 = F_5 + F_6
-\end{equation}
-\begin{equation}
-    \label{eq:example_var1}
-    0 \leq F_i \leq 10 \quad \forall i \in \{1,...,7\}
-\end{equation}
-\begin{equation}
-    \label{eq:example_var2}
-    0 \leq C_S \leq C_S^{max}
-\end{equation}
-\begin{equation}
-    \label{eq:example_var3}
-    C_R^{min} \leq C_R \leq C_R^{max}
-\end{equation}
-\vskip 6pt
+    \end{bmatrix} \\
+    & F_1 = F_2 + F_3 \\
+    & F_7 = F_5 + F_6 \\
+    & 0 \leq F_i \leq 10 \quad \forall i \in \{1,...,7\} \\
+    & 0 \leq C_S \leq C_S^{max} \\
+    & C_R^{min} \leq C_R \leq C_R^{max}
+\end{align*}
 
@@
 \end{lstlisting}
-    \item Define the outer disjunctions.
+    \item Define the outer disjunctions for the reaction pathway selection.
 \begin{lstlisting}[language = Julia]

### 2024-10-03 src/reformulate.jl
Update error messages

@@ -78,8 +78,9 @@ function _reformulate_disjunctions(model::JuMP.AbstractModel, method::AbstractRe
         dref = DisjunctionRef(model, idx)
         if requires_exactly1(method) && !haskey(gdp_data(model).exactly1_constraints, dref) &&
             !any(has_logical_compliment.(disj.constraint.indicators))
-            error("Reformulation method `$method` requires disjunctions where only 1 disjunct is selected, " *
-                  "but `exactly1 = false` for disjunction `$dref`.")
+            error("Reformulation method `$method` requires disjunctions where only 1 disjunct is selected, ",
+                  "but `exactly1 = false` or none of the logical variables are logical compliments ",
+                  "for disjunction `$dref`.")
         end
         if requires_variable_bound_info(method)
             for vref in _get_disjunction_variables(model, disj.constraint)

### 2024-10-03 src/variables.jl

@@ -35,11 +35,14 @@ function JuMP.build_variable(
     elseif info.has_start && !isone(info.start) && !iszero(info.start)
         _error("Invalid start value, must be false or true.")
     elseif (info.has_start || info.has_fix) && !isnothing(logical_compliment)
-        _error("Cannot fix or provide a start value for logical variable " *
-               "that has a logical compliment variable.")
+        _error("Cannot fix or provide a start value for a logical variable " *
+               "that is a logical compliment variable. Try adding these " *
+               "properties to the variable it is the compliment of.")
     elseif !isnothing(logical_compliment) && has_logical_compliment(logical_compliment)
         _error("Cannot specify a logical compliment that itself is a " *
-               "logical compliment.")
+               "logical compliment. For two logical variables that " *
+               "are the compliment of one another, only use the " * 
+               "`logical_compliment` argument on one of them.")
     end
 
     # create the variable
@@ -227,7 +230,8 @@ function JuMP.set_start_value(
     value::Union{Nothing, Bool}
     )
     if has_logical_compliment(vref)
-        error("Cannot set the start value of a variable with a logical compliment.")
+        error("Cannot set the start value of a logical compliment variable. ",
+              "Try setting the start value of its logical compliment instead.")
     end
     new_var = LogicalVariable(JuMP.fix_value(vref), value, nothing)
     _set_variable_object(vref, new_var)
@@ -263,7 +267,8 @@ new one.
 """
 function JuMP.fix(vref::LogicalVariableRef, value::Bool)
     if has_logical_compliment(vref)
-        error("Cannot fix value of a variable with a logical compliment.")
+        error("Cannot fix value of a logical variable compliment. ",
+             "Try fixing its logical compliment instead.")
     end
     new_var = LogicalVariable(value, JuMP.start_value(vref), nothing)
     _set_variable_object(vref, new_var)

### 2024-10-03 src/constraints.jl
Update terminology

@@ -302,17 +302,17 @@ function _check_disjunction(
             _error("`$lvref` is not a valid logical variable reference.")
         end
     end
-    if length(lvrefs) != 2 && any(has_logical_compliment.(lvrefs))
-        _error("Can only use logical compliment variables in Disjunctions " *
+    if length(lvrefs) != 2 && any(has_logical_complement.(lvrefs))
+        _error("Can only use logical complement variables in Disjunctions " *
                "with two disjuncts.")
-    elseif length(lvrefs) == 2 && any(has_logical_compliment.(lvrefs))
+    elseif length(lvrefs) == 2 && any(has_logical_complement.(lvrefs))
         T = JuMP.value_type(M)
         V = JuMP.variable_ref_type(M)
         expr1 = convert(JuMP.GenericAffExpr{T, V}, binary_variable(first(lvrefs)))
         expr2 = 1 - binary_variable(last(lvrefs))
         if !JuMP.isequal_canonical(expr1, expr2)
-            _error("When using logical compliment variables in a disjunction, " *
-                   "both logical variables must be the compliment of one another.")
+            _error("When using logical complement variables in a disjunction, " *
+                   "both logical variables must be the complement of one another.")
         end
     end
     return lvrefs
@@ -366,7 +366,7 @@ function _disjunction(
     # create the disjunction
     dref = _create_disjunction(_error, model, structure, name, false)
     # add the exactly one constraint if desired
-    if exactly1 && !any(has_logical_compliment.(structure))
+    if exactly1 && !any(has_logical_complement.(structure))
         lvars = JuMP.constraint_object(dref).indicators
         func = JuMP.model_convert.(model, Any[1, lvars...])
         set = _MOIExactly(length(lvars) + 1)
@@ -402,9 +402,9 @@ function _disjunction(
     for (kwarg, _) in extra_kwargs
         _error("Unrecognized keyword argument $kwarg.")
     end
-    # check that no logical compliment is used
-    if any(has_logical_compliment.(structure))
-        _error("Logical compliment variables are not supported for " *
+    # check that no logical complement is used
+    if any(has_logical_complement.(structure))
+        _error("Logical complement variables are not supported for " *
                "use in nested disjunctions.")
     end
     # create the disjunction
@@ -412,7 +412,7 @@ function _disjunction(
     obj = constraint_object(dref)
     _add_indicator_var(_DisjunctConstraint(obj, tag.indicator), dref, model)
[…]

### 2024-10-03 src/datatypes.jl

@@ -31,13 +31,13 @@ A variable type the logical variables associated with disjuncts in a [`Disjuncti
 **Fields**
 - `fix_value::Union{Nothing, Bool}`: A fixed boolean value if there is one.
 - `start_value::Union{Nothing, Bool}`: An initial guess if there is one.
-- `logical_compliment::Union{Nothing, LogicalVariableRef}`: The logical compliment of
+- `logical_complement::Union{Nothing, LogicalVariableRef}`: The logical complement of
    this variable if there is one.
 """
 struct LogicalVariable <: JuMP.AbstractVariable 
     fix_value::Union{Nothing, Bool}
     start_value::Union{Nothing, Bool}
-    logical_compliment::Union{Nothing, LogicalVariableRef}
+    logical_complement::Union{Nothing, LogicalVariableRef}
 end
 
 # Wrapper variable type for including arbitrary tags that will be used for 

### 2024-10-03 src/reformulate.jl

@@ -77,9 +77,9 @@ function _reformulate_disjunctions(model::JuMP.AbstractModel, method::AbstractRe
         disj.constraint.nested && continue #only reformulate top level disjunctions
         dref = DisjunctionRef(model, idx)
         if requires_exactly1(method) && !haskey(gdp_data(model).exactly1_constraints, dref) &&
-            !any(has_logical_compliment.(disj.constraint.indicators))
+            !any(has_logical_complement.(disj.constraint.indicators))
             error("Reformulation method `$method` requires disjunctions where only 1 disjunct is selected, ",
-                  "but `exactly1 = false` or none of the logical variables are logical compliments ",
+                  "but `exactly1 = false` or none of the logical variables are logical complements ",
                   "for disjunction `$dref`.")
         end
         if requires_variable_bound_info(method)

### 2024-10-03 src/variables.jl

@@ -6,20 +6,20 @@
         _error::Function,
         info::JuMP.VariableInfo, 
         ::Union{Type{Logical}, Logical};
-        [logical_compliment::Union{Nothing, LogicalVariableRef} = nothing]
+        [logical_complement::Union{Nothing, LogicalVariableRef} = nothing]
         )::LogicalVariable
 
 Extend `JuMP.build_variable` to work with logical variables. This in 
 combination with `JuMP.add_variable` enables the use of 
-`@variable(model, [var_expr], Logical)`. Optionally, a `logical_compliment`
-can be given which provides a logical variable that is the compliment of this
+`@variable(model, [var_expr], Logical)`. Optionally, a `logical_complement`
+can be given which provides a logical variable that is the complement of this
 one (common for disjunctions with two disjuncts).
 """
 function JuMP.build_variable(
     _error::Function, 
     info::JuMP.VariableInfo, 
     tag::Type{Logical};
-    logical_compliment::Union{Nothing, LogicalVariableRef} = nothing,
+    logical_complement::Union{Nothing, LogicalVariableRef} = nothing,
     kwargs...
     )
     # check for invalid input
@@ -34,21 +34,21 @@ function JuMP.build_variable(
         _error("Invalid fix value, must be false or true.")
     elseif info.has_start && !isone(info.start) && !iszero(info.start)
         _error("Invalid start value, must be false or true.")
-    elseif (info.has_start || info.has_fix) && !isnothing(logical_compliment)
+    elseif (info.has_start || info.has_fix) && !isnothing(logical_complement)
         _error("Cannot fix or provide a start value for a logical variable " *
-               "that is a logical compliment variable. Try adding these " *
-               "properties to the variable it is the compliment of.")
-    elseif !isnothing(logical_compliment) && has_logical_compliment(logical_compliment)
-        _error("Cannot specify a logical compliment that itself is a " *
-               "logical compliment. For two logical variables that " *
-               "are the compliment of one another, only use the " * 
-               "`logical_compliment` argument on one of them.")
+               "that is a logical complement variable. Add these " *
+               "properties to the variable that is its complement.")
+    elseif !isnothing(logical_complement) && has_logical_complement(logical_complement)
+        _error("Cannot specify a logical complement that itself is a " *
[…]

### 2024-10-03 test/constraints/disjunction.jl

@@ -39,7 +39,7 @@ function test_disjunction_add_fail()
     @constraint(model, [i = 1:2], x == 5, Disjunct(w[i]))
     @test_throws ErrorException disjunction(model, w, Disjunct(w[3]), bad_key = 42)
 
-    @variable(model, yc[i = 1:2], Logical, logical_compliment = y[i])
+    @variable(model, yc[i = 1:2], Logical, logical_complement = y[i])
     @test_throws ErrorException disjunction(model, [yc[1]])
     @test_throws ErrorException disjunction(model, [yc[1], y[2]])
     @test_throws ErrorException disjunction(model, [y[1], yc[1]], Disjunct(y[2]))

### 2024-10-03 test/solve.jl

@@ -1,11 +1,11 @@
 using HiGHS
 
-function test_linear_gdp_example(m, use_compliments = false)
+function test_linear_gdp_example(m, use_complements = false)
     set_attribute(m, MOI.Silent(), true)
     @variable(m, 1 ≤ x[1:2] ≤ 9)
-    if use_compliments
+    if use_complements
         @variable(m, Y1, Logical)
-        @variable(m, Y2, Logical, logical_compliment = Y1)
+        @variable(m, Y2, Logical, logical_complement = Y1)
         Y = [Y1, Y2]
     else
         @variable(m, Y[1:2], Logical)
@@ -40,7 +40,7 @@ function test_linear_gdp_example(m, use_compliments = false)
     @test value(variable_by_name(m, "x[1]_W[2]")) ≈ 0
     @test value(variable_by_name(m, "x[2]_W[1]")) ≈ 0
     @test value(variable_by_name(m, "x[2]_W[2]")) ≈ 0
-    if !use_compliments
+    if !use_complements
         @test value(variable_by_name(m, "x[1]_Y[1]")) ≈ 0
         @test value(variable_by_name(m, "x[1]_Y[2]")) ≈ 9
         @test value(variable_by_name(m, "x[2]_Y[1]")) ≈ 0

### 2024-10-03 test/variables/logical.jl

@@ -131,13 +131,13 @@ function test_lvar_delete()
     @test !is_valid(model, bvar)
 end
 
-function test_lvar_logical_compliment()
+function test_lvar_logical_complement()
     model = GDPModel()
     @variable(model, y1, Logical)
     # test addition
-    @test_throws ErrorException @variable(model, y2 == true, Logical, logical_compliment = y1)
-    @test_throws ErrorException @variable(model, y2, Logical, logical_compliment = y1, start = false)
-    @variable(model, y2, Logical, logical_compliment = y1)
+    @test_throws ErrorException @variable(model, y2 == true, Logical, logical_complement = y1)
+    @test_throws ErrorException @variable(model, y2, Logical, logical_complement = y1, start = false)
+    @variable(model, y2, Logical, logical_complement = y1)
     # test queries
     @test binary_variable(y2) == 1 - binary_variable(y1)
     @test name(y2) == "y2"
@@ -146,10 +146,10 @@ function test_lvar_logical_compliment()
     @test_throws ErrorException set_start_value(y2, false)
     @test_throws ErrorException fix(y2, false)
     @test unfix(y2) isa Nothing
-    @test has_logical_compliment(y2)
-    @test !has_logical_compliment(y1)
+    @test has_logical_complement(y2)
+    @test !has_logical_complement(y1)
     # test error for logical of logical
-    @test_throws ErrorException @variable(model, y3, Logical, logical_compliment = y2)
+    @test_throws ErrorException @variable(model, y3, Logical, logical_complement = y2)
     # test deletion
     @test delete(model, y2) isa Nothing
     @test !is_valid(model, y2)
@@ -202,7 +202,7 @@ end
         test_lvar_delete()
     end
     @testset "Logical Compliment Variables" begin
-        test_lvar_logical_compliment()
+        test_lvar_logical_complement()
     end
     @testset "Tagged Logical Variables" begin
         test_tagged_variables()

### 2024-10-03 test/constraints/indicator.jl
fix typo

@@ -131,11 +131,11 @@ function test_extension_indicator()
     @test all([cobj.set isa MOI.Indicator for cobj in ref_cons_obj])
 end
 
-function test_indicator_compliment()
+function test_indicator_complement()
     model = GDPModel()
     @variable(model, x)
     @variable(model, y1, Logical)
-    @variable(model, y2, Logical, logical_compliment = y1)
+    @variable(model, y2, Logical, logical_complement = y1)
     y = [y1, y2]
     @constraint(model, x == 5, Disjunct(y[1]))
     @constraint(model, x <= 5, Disjunct(y[1]))
@@ -157,7 +157,7 @@ function test_indicator_compliment()
     A = [1 0; 0 1]
     @variable(model, x)
     @variable(model, y1, Logical)
-    @variable(model, y2, Logical, logical_compliment = y1)
+    @variable(model, y2, Logical, logical_complement = y1)
     y = [y1, y2]
     @constraint(model, A*[x,x] == [5,5], Disjunct(y[1]))
     @constraint(model, A*[x,x] <= [0,0], Disjunct(y[2]))
@@ -180,5 +180,5 @@ end
     test_indicator_sparse_axis()
     test_indicator_nested()
     test_extension_indicator()
-    test_indicator_compliment()
+    test_indicator_complement()
 end

### 2024-10-04 src/reformulate.jl
Support Logical Complements (#118)
* Support logical compliments

* Update error messages

* Update terminology

* fix typo

@@ -76,9 +76,11 @@ function _reformulate_disjunctions(model::JuMP.AbstractModel, method::AbstractRe
     for (idx, disj) in _disjunctions(model)
         disj.constraint.nested && continue #only reformulate top level disjunctions
         dref = DisjunctionRef(model, idx)
-        if requires_exactly1(method) && !haskey(gdp_data(model).exactly1_constraints, dref)
-            error("Reformulation method `$method` requires disjunctions where only 1 disjunct is selected, " *
-                  "but `exactly1 = false` for disjunction `$dref`.")
+        if requires_exactly1(method) && !haskey(gdp_data(model).exactly1_constraints, dref) &&
+            !any(has_logical_complement.(disj.constraint.indicators))
+            error("Reformulation method `$method` requires disjunctions where only 1 disjunct is selected, ",
+                  "but `exactly1 = false` or none of the logical variables are logical complements ",
+                  "for disjunction `$dref`.")
         end
         if requires_variable_bound_info(method)
             for vref in _get_disjunction_variables(model, disj.constraint)
@@ -94,7 +96,7 @@ function _reformulate_disjunctions(model::JuMP.AbstractModel, method::AbstractRe
     end
 end
 
-# disjuncts
+# individual disjunctions
 """
     reformulate_disjunction(
         model::JuMP.AbstractModel, 
@@ -137,7 +139,7 @@ end
     reformulate_disjunct_constraint(
         model::JuMP.AbstractModel,  
         con::JuMP.AbstractConstraint, 
-        bvref::JuMP.AbstractVariableRef,
+        bvref::Union{JuMP.AbstractVariableRef, JuMP.GenericAffExpr},
         method::AbstractReformulationMethod
     )
 
@@ -148,7 +150,7 @@ constraint. If `method` needs to specify how to reformulate the entire disjuncti
 function reformulate_disjunct_constraint(
     model::JuMP.AbstractModel,  
     con::Disjunction, 
-    bvref::JuMP.AbstractVariableRef,
+    bvref::Union{JuMP.AbstractVariableRef, JuMP.GenericAffExpr},
     method::AbstractReformulationMethod
 )
     ref_cons = reformulate_disjunction(model, con, method)
@@ -163,7 +165,7 @@ end
 function reformulate_disjunct_constraint(
     model::JuMP.AbstractModel,  
     con::JuMP.AbstractConstraint, 
-    bvref::JuMP.AbstractVariableRef,
[…]

### 2024-10-04 test/constraints/disjunction.jl

@@ -38,6 +38,11 @@ function test_disjunction_add_fail()
     @variable(model, w[1:3], Logical)
     @constraint(model, [i = 1:2], x == 5, Disjunct(w[i]))
     @test_throws ErrorException disjunction(model, w, Disjunct(w[3]), bad_key = 42)
+
+    @variable(model, yc[i = 1:2], Logical, logical_complement = y[i])
+    @test_throws ErrorException disjunction(model, [yc[1]])
+    @test_throws ErrorException disjunction(model, [yc[1], y[2]])
+    @test_throws ErrorException disjunction(model, [y[1], yc[1]], Disjunct(y[2]))
 end
 
 function test_disjunction_add_success()

### 2024-10-04 test/solve.jl

@@ -1,9 +1,15 @@
 using HiGHS
 
-function test_linear_gdp_example(m)
+function test_linear_gdp_example(m, use_complements = false)
     set_attribute(m, MOI.Silent(), true)
     @variable(m, 1 ≤ x[1:2] ≤ 9)
-    @variable(m, Y[1:2], Logical)
+    if use_complements
+        @variable(m, Y1, Logical)
+        @variable(m, Y2, Logical, logical_complement = Y1)
+        Y = [Y1, Y2]
+    else
+        @variable(m, Y[1:2], Logical)
+    end
     @variable(m, W[1:2], Logical)
     @objective(m, Max, sum(x))
     @constraint(m, y1[i=1:2], [1,4][i] ≤ x[i] ≤ [3,6][i], Disjunct(Y[1]))
@@ -30,14 +36,16 @@ function test_linear_gdp_example(m)
     @test value(Y[2])
     @test !value(W[1])
     @test !value(W[2])
-    @test value(variable_by_name(m, "x[1]_Y[1]")) ≈ 0
-    @test value(variable_by_name(m, "x[1]_Y[2]")) ≈ 9
     @test value(variable_by_name(m, "x[1]_W[1]")) ≈ 0
     @test value(variable_by_name(m, "x[1]_W[2]")) ≈ 0
-    @test value(variable_by_name(m, "x[2]_Y[1]")) ≈ 0
-    @test value(variable_by_name(m, "x[2]_Y[2]")) ≈ 2
     @test value(variable_by_name(m, "x[2]_W[1]")) ≈ 0
     @test value(variable_by_name(m, "x[2]_W[2]")) ≈ 0
+    if !use_complements
+        @test value(variable_by_name(m, "x[1]_Y[1]")) ≈ 0
+        @test value(variable_by_name(m, "x[1]_Y[2]")) ≈ 9
+        @test value(variable_by_name(m, "x[2]_Y[1]")) ≈ 0
+        @test value(variable_by_name(m, "x[2]_Y[2]")) ≈ 2
+    end
 end
 
 function test_generic_model(m)
@@ -55,12 +63,14 @@ function test_generic_model(m)
 
     @test optimize!(m, gdp_method = BigM()) isa Nothing
     @test optimize!(m, gdp_method = Hull()) isa Nothing
+    @test optimize!(m, gdp_method = Indicator()) isa Nothing
 
     # TODO add meaningful tests to check the constraints/variables
 end
 
[…]

### 2024-10-04 test/variables/logical.jl

@@ -30,7 +30,7 @@ function test_lvar_add_success()
     @test isnothing(fix_value(y))
     @test isequal_canonical(y, copy(y))
     @test haskey(DP._logical_variables(model), index(y))
-    @test DP._logical_variables(model)[index(y)].variable == LogicalVariable(nothing, nothing)
+    @test DP._logical_variables(model)[index(y)].variable == LogicalVariable(nothing, nothing, nothing)
     @test DP._logical_variables(model)[index(y)].name == "y"
     @test binary_variable(y) isa VariableRef
     @test is_binary(binary_variable(y))
@@ -131,6 +131,30 @@ function test_lvar_delete()
     @test !is_valid(model, bvar)
 end
 
+function test_lvar_logical_complement()
+    model = GDPModel()
+    @variable(model, y1, Logical)
+    # test addition
+    @test_throws ErrorException @variable(model, y2 == true, Logical, logical_complement = y1)
+    @test_throws ErrorException @variable(model, y2, Logical, logical_complement = y1, start = false)
+    @variable(model, y2, Logical, logical_complement = y1)
+    # test queries
+    @test binary_variable(y2) == 1 - binary_variable(y1)
+    @test name(y2) == "y2"
+    @test set_name(y2, "new_name") isa Nothing
+    @test name(y2) == "new_name"
+    @test_throws ErrorException set_start_value(y2, false)
+    @test_throws ErrorException fix(y2, false)
+    @test unfix(y2) isa Nothing
+    @test has_logical_complement(y2)
+    @test !has_logical_complement(y1)
+    # test error for logical of logical
+    @test_throws ErrorException @variable(model, y3, Logical, logical_complement = y2)
+    # test deletion
+    @test delete(model, y2) isa Nothing
+    @test !is_valid(model, y2)
+end
+
 function test_tagged_variables()
     model = GDPModel{MyModel, MyVarRef, MyConRef}()
     y = [LogicalVariableRef(model, LogicalVariableIndex(i)) for i in 1:2]
@@ -176,6 +200,9 @@ end
     end
     @testset "Delete Logical Variables" begin
         test_lvar_delete()
+    end
+    @testset "Logical Compliment Variables" begin
+        test_lvar_logical_complement()
     end
     @testset "Tagged Logical Variables" begin
         test_tagged_variables()

### 2024-10-04 paper/header.tex

% **************GENERATED FILE, DO NOT EDIT**************

\title{DisjunctiveProgramming.jl: Generalized Disjunctive Programming Models and Algorithms for JuMP}

\author[1]{Hector D. Perez}
\author[1]{Shivank Joshi}
\author[1]{Ignacio E. Grossmann}
\affil[1]{Carnegie Mellon University}

\keywords{JuMP, Mathematical Optimization, Generalized Disjunctive Programming}

\hypersetup{
pdftitle = {DisjunctiveProgramming.jl: Generalized Disjunctive Programming Models and Algorithms for JuMP},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Hector D. Perez, Shivank Joshi, Ignacio E. Grossmann},
pdfkeywords = {JuMP, Mathematical Optimization, Generalized Disjunctive Programming},
}

### 2024-10-04 paper/paper.tex

@@
 
-\subsection{Solution Technique: Reformulation to Mixed-Integer Program}
+\subsection{Solution Technique: Reformulation to Mixed-Integer Program} \label{reformulation}
 The simplest example of a linear GDP system is given below, where $Y_i$ is a Boolean indicator variable that enforces the constraints in the disjunct ($Ax \le b$ or $Cx \le d$) when $true$,
@@
 
-Exclusive-OR constraints as the one given in Eq. \eqref{eq:simple_xor} are more generally modeled as $exactly(1,\{Y_1,Y_2\})$.
+Exclusive-OR constraints as the one used in Section \ref{reformulation} are more generally modeled as $exactly(1,\{Y_1,Y_2\})$.
 

### 2024-10-04 dev/search_index.js
build based on 7bbee0c

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"api/#API","page":"API","title":"API","text":"","category":"section"},{"location":"api/","page":"API","title":"API","text":"Modules = [DisjunctiveProgramming]\nOrder   = [:macro, :function, :type]","category":"page"},{"location":"api/#DisjunctiveProgramming.@disjunction-Tuple","page":"API","title":"DisjunctiveProgramming.@disjunction","text":"@disjunction(model, expr, kw_args...)\n\nAdd a disjunction described by the expression expr,  which must be a Vector of LogicalVariableRefs.\n\n@disjunction(model, ref[i=..., j=..., ...], expr, kw_args...)\n\nAdd a group of disjunction described by the expression expr parameterized by i, j, ..., which must be a Vector of LogicalVariableRefs. \n\nIn both of the above calls, a Disjunct tag can be added to create  nested disjunctions.\n\nThe recognized keyword arguments in kw_args are the following:\n\nbase_name: Sets the name prefix used to generate constraint names.    It corresponds to the constraint name for scalar constraints, otherwise,    the constraint names are set to base_name[...] for each index ...        of the axes axes.\ncontainer: Specify the container type.\nexactly1: Specify a Bool whether a constraint should be added to   only allow selecting one disjunct in the disjunction.\n\nTo create disjunctions without macros, see disjunction.\n\n\n\n\n\n","category":"macro"},{"location":"api/#DisjunctiveProgramming.@disjunctions-Tuple{Any, Any}","page":"API","title":"DisjunctiveProgramming.@disjunctions","text":"@disjunctions(model, args...)\n\nAdds groups of disjunctions at once, in the same fashion as the @disjunction macro.\n\nThe model must be the first argument, and multiple disjunctions can be added on multiple  lines wrapped in a begin ... end block.\n\nThe macro returns a tuple containing the disjunctions that were defined.\n\nExample\n\njulia model = GDPModel(); @variable(model, w); @variable(model, x); @variable(model, Y[1:4], LogicalVariable); @constraint(model, [i=1:2], w == i, Disjunct(Y[i])); @constraint(model, [i=3:4], x == i, Disjunct(Y[i])); @disjunctions(model, begin     [Y[1], Y[2]]     [Y[3], Y[4]] end);`\n\n\n\n\n\n","category":"macro"},{"location":"api/#DisjunctiveProgramming.binary_variable-T
[…]
